---
title: "Initial Analyses"
author: "Will Schulz"
date: "2023-08-21"
output: html_document
---


```{r}
run_stan = T
set.seed(4711)

```


```{r}
library(tidyverse)
library(haven)
library(pewmethods)
library(rstan)
library(stargazer)
#library(imager)
library(progress)
```



# Appendix A Stuff


```{r}
d_591 <- read_csv(file="../data/591_exploratory.csv")[-c(1:2),] %>% filter(consentStatement=="I would like to participate." & Status!="Survey Preview")

d_591$ideology <- d_591$postIdeoL
d_591$ideology[which(is.na(d_591$ideology))] <- d_591$postIdeoC[which(is.na(d_591$ideology))]


d_591 <- d_591 %>% mutate(ideology = case_when(ideology == "Very Liberal" ~ -2,
                                               ideology == "Liberal" ~ -1,
                                               ideology == "Moderate" ~ 0,
                                               ideology == "Conservative" ~ 1,
                                               ideology == "Very Conservative" ~ 2),
                          polInt = case_when(Q59 == "Not interested at all" ~ -2,
                                             Q59 == "Slightly interested" ~ -1,
                                             Q59 == "Moderately interested" ~ 0,
                                             Q59 == "Interested" ~ 1,
                                             Q59 == "Very interested" ~ 2),
                          strongDem = case_when(Q56 == "Not very strong Democrat" ~ 0,
                                                Q56 == "Strong Democrat" ~ 1),
                          mainSM = case_when(str_detect(string = whichSM, pattern = "Twitter|Facebook|Instagram") ~ 1,
                                             str_detect(string = whichSM, pattern = "Twitter|Facebook|Instagram", negate = T) ~ 0)
)

d_591 <- d_591 %>% drop_na(ideology, mainSM, youPartisan, othersPartisan)
d_591 <- d_591 %>% filter(mainSM==1)

d_591
```



```{r}
# careOrder <- c("Don't care at all","Care a little bit","Care somewhat","Care a great deal")
# likelyOrder <- c("Much more likely","Somewhat more likely","Neither more likely nor less likely","Somewhat less likely","Much less likely")
partisanOrder <- c("Much less partisan on social media","Somewhat less partisan on social media","Neither more nor less partisan on social media","Somewhat more partisan on social media","Much more partisan on social media")
# 
# toplot <- d_591 %>% select(You=youPartisan, Others=othersPartisan) %>% gather(key = items, value = Answer) %>% mutate(Answer=factor(Answer, levels=partisanOrder))
# toplot <- toplot %>% group_by(items) %>% summarise(more_partisan = mean(Answer %in% c("Somewhat more partisan on social media", "Much more partisan on social media")))
# 
# pdf(file = "../results/591_partisan_base.pdf", width = 8.25, height = 4.5)
# par(mar = c(5.1, 6.1, 2.1, 4.1))
# barplot(more_partisan ~ items, data = toplot, xlab = "Third/First-Person Wording", ylab = "Much + Somewhat MORE Partisan Online", ylim = c(0,1), space = 1, main = "Do You/Others Act More/Less Partisan Online Than Off?", border = NA)
# dev.off()
# 
# toplot
```


```{r}
short_xlab_names_591= c("Much\nLess","Somewhat\nLess","Neither","Somewhat\nMore","Much\nMore")

w_appendix_hists = 6
h_appendix_hists = 4

pdf("../results/591_partisanhist_others.pdf", width = w_appendix_hists, height = h_appendix_hists)
d_591 %>% select(You=youPartisan, Others=othersPartisan) %>% gather(key = items, value = Answer) %>% mutate(Answer=factor(Answer, levels=partisanOrder)) %>% group_by(items, Answer) %>% summarize(count=n()) %>% filter(items=="Others") %>% ungroup() %>% pull(count, Answer) %>% {./sum(.)}  %>% barplot(height =., main = "", names.arg = short_xlab_names_591)
dev.off()

pdf("../results/591_partisanhist_you.pdf", width = w_appendix_hists, height = h_appendix_hists)
d_591 %>% select(You=youPartisan, Others=othersPartisan) %>% gather(key = items, value = Answer)%>% mutate(Answer=factor(Answer, levels=partisanOrder)) %>% group_by(items, Answer) %>% summarize(count=n()) %>% filter(items=="You") %>% ungroup() %>% pull(count, Answer) %>% {./sum(.)} %>% barplot(height =., main = "", names.arg = short_xlab_names_591)
dev.off()

```


# Read In Raw Data

```{r}
raw_data <- read_sav("../data/9089.121_TESS_Schulz_FinalData_Updated.sav")

sa_num_raw <- raw_data %>% select(starts_with("Q6")) %>% as.matrix

#drop NA rows
rowmean_na <- (apply(sa_num_raw, MARGIN = 1, FUN = function(x){mean(is.na(x))}))
#unique(rowmean_na)

rows_todrop <- which(rowmean_na!=0)
raw_data <- raw_data[-rows_todrop,]
sa_num_raw <- sa_num_raw[-rows_todrop,]
```


# Look at Stuff for Explaining Procedure

## Process Q1 and Q2

Q1: Do you use any of the following social media platforms?

GRID ITEMS, RANDOMIZE:
A.	Facebook
B.	Snapchat
C.	TikTok
D.	Instagram
E.	WhatsApp
F.	Discord
G.	Twitter
H.	YouTube
I.	BeReal
J.	Mastodon

RESPONSE OPTIONS:
01	Yes
02	No


Q2: "Do you use any of the following social media platforms to post your opinions about politics or current events?"

[CAWI - REMOVE BOLD] <i> Please select all that apply. </i>
[CATI] SELECT ALL THAT APPLY.

GRID ITEMS:
1.	[SHOW IF Q1A=1] Facebook
2.	[SHOW IF Q1B=1] Snapchat
3.	[SHOW IF Q1C=1] TikTok
4.	[SHOW IF Q1D=1] Instagram
5.	[SHOW IF Q1E=1] WhatsApp
6.	[SHOW IF Q1F=1] Discord
7.	[SHOW IF Q1G=1] Twitter
8.	[SHOW IF Q1H=1] YouTube
9.	[SHOW IF Q1I=1] BeReal
10.	[SHOW IF Q1J=1] Mastodon


RESPONSE OPTIONS:
1.	Yes
2.	 No


```{r}
q1_platforms <- c("Facebook", "Snapchat", "TikTok", "Instagram", "WhatsApp", "Discord", "Twitter", "YouTube", "BeReal", "Mastodon")

```


```{r}
# Use mutate_at with case_when
raw_data <- raw_data %>%
  mutate_at(
    vars(starts_with("Q1")),
    funs(
      case_when(
        . == 1 ~ TRUE,      # If the value is >= 30, double it
        . == 2 ~ FALSE, # If the value is between 20 and 29 (inclusive), keep it as is
        ! . %in% c(1,2) ~ NA      # Otherwise, set it to NA
      )
    )
  )


raw_data <- raw_data %>%
  mutate_at(
    vars(starts_with("Q2")),
    funs(
      case_when(
        . == 1 ~ TRUE,      # If the value is >= 30, double it
        . == 2 ~ FALSE, # If the value is between 20 and 29 (inclusive), keep it as is
        ! . %in% c(1,2) ~ NA      # Otherwise, set it to NA
      )
    )
  )

colnames(raw_data)[which(str_starts(string = colnames(raw_data), pattern = "Q1"))] <- paste0("use_",q1_platforms)

q2_platforms <- q1_platforms

colnames(raw_data)[which(str_starts(string = colnames(raw_data), pattern = "Q2"))] <- paste0("post_",q2_platforms)

raw_data
```


```{r}
# raw_data %>% filter(use_Twitter) %>% select(post_Twitter)
# 
# raw_data %>% filter(!use_Twitter) %>% select(post_Twitter)
# 
# 
# raw_data %>% filter(use_Twitter|use_Facebook) %>% select(starts_with("post_"))

```


DOV_ASSIGNED:
1 FB Poster
2 FB Lurker
3 TW Poster
4 TW Lurker


```{r}
# raw_data %>% filter(use_Facebook & post_Facebook) %>% select(starts_with("DOV_"))
# raw_data %>% filter(use_Facebook & !post_Facebook) %>% select(starts_with("DOV_"))
# 
# 
# raw_data %>% filter(use_Twitter & post_Twitter) %>% select(starts_with("DOV_"))
# raw_data %>% filter(use_Facebook & !post_Facebook) %>% select(starts_with("DOV_"))

```



```{r}
raw_data <- raw_data %>%
  mutate_at(
    vars(starts_with("DOV_")),
    funs(
      as.numeric(.)
    )
  )

raw_data <- raw_data %>%
  mutate_at(
    vars(starts_with("DOV_ELIG_")),
    funs(
      as.logical(.)
    )
  )

```

```{r}
fb_logocolor = "#4267B2"
tw_logocolor = "#1DA1F2"

ch3_colors_fbtwlposterlurker <- c("fb_poster" = fb_logocolor, "fb_lurker" = adjustcolor(fb_logocolor, alpha = .5), "tw_poster" = tw_logocolor,"tw_lurker" =  adjustcolor(tw_logocolor, alpha = .5))
```


```{r}
raw_data %>% filter(DOV_ELIG_1) %>% pull(DOV_ASSIGNED) %>% {.==1} %>% mean #FB Poster
raw_data %>% filter(DOV_ELIG_2) %>% pull(DOV_ASSIGNED) %>% {.==2} %>% mean #FB Lurker
raw_data %>% filter(DOV_ELIG_3) %>% pull(DOV_ASSIGNED) %>% {.==3} %>% mean #TW Poster
raw_data %>% filter(DOV_ELIG_4) %>% pull(DOV_ASSIGNED) %>% {.==4} %>% mean #TW Lurker

```


```{r}
# pies: assignment by eligibility

d_to_summarise_assignment <- raw_data %>% mutate(DOV_ASSIGNED = fct_case_when(DOV_ASSIGNED == 1 ~ "Facebook Poster",
                                                                              DOV_ASSIGNED == 2 ~ "Facebook Lurker",
                                                                              DOV_ASSIGNED == 3 ~ "Twitter Poster",
                                                                              DOV_ASSIGNED == 4 ~ "Twitter Lurker")) %>%
  group_by(DOV_ASSIGNED) %>% summarise(elig_fbposter = sum(DOV_ELIG_1==1),
                                       elig_fblurker = sum(DOV_ELIG_2==1),
                                       elig_twposter = sum(DOV_ELIG_3==1),
                                       elig_twlurker = sum(DOV_ELIG_4==1)
  )

elig_fbposter_assignment <- d_to_summarise_assignment %>% {setNames(.$elig_fbposter, if_else(.$elig_fbposter>0, .$DOV_ASSIGNED, ""))}
elig_fblurker_assignment <- d_to_summarise_assignment %>% {setNames(.$elig_fblurker, if_else(.$elig_fblurker>0, .$DOV_ASSIGNED, ""))}
elig_twposter_assignment <- d_to_summarise_assignment %>% {setNames(.$elig_twposter, if_else(.$elig_twposter>0, .$DOV_ASSIGNED, ""))}
elig_twlurker_assignment <- d_to_summarise_assignment %>% {setNames(.$elig_twlurker, if_else(.$elig_twlurker>0, .$DOV_ASSIGNED, ""))}

par(mfrow=c(1,4))
elig_fbposter_assignment %>% pie(main = "Eligible Facebook Posters",
                                 col = ch3_colors_fbtwlposterlurker)
elig_fblurker_assignment %>% pie(main = "Eligible Facebook Lurkers",
                                 col = ch3_colors_fbtwlposterlurker)
elig_twposter_assignment %>% pie(main = "Eligible Twitter Posters",
                                 col = ch3_colors_fbtwlposterlurker)
elig_twlurker_assignment %>% pie(main = "Eligible Twitter Lurkers",
                                 col = ch3_colors_fbtwlposterlurker)
```





```{r}
# # pies: eligibility by assignment
# 
# d_to_summarise_assignment2 <- d_to_summarise_assignment %>% select(starts_with("elig_")) %>% t
# colnames(d_to_summarise_assignment2) <- gsub(pattern = " ", replacement = "_",d_to_summarise_assignment$DOV_ASSIGNED)
# d_to_summarise_assignment2 <- as.data.frame(d_to_summarise_assignment2) %>% mutate(eligibility = d_to_summarise_assignment$DOV_ASSIGNED, .before = 0)
# 
# d_to_summarise_assignment2$
# 
# ass_fbposter_eligibility <- d_to_summarise_assignment2 %>% {setNames(.$Facebook_Poster, if_else(.$Facebook_Poster>0, .$eligibility, ""))}
# ass_fblurker_eligibility <- d_to_summarise_assignment2 %>% {setNames(.$Facebook_Lurker, if_else(.$Facebook_Lurker>0, .$eligibility, ""))}
# ass_twposter_eligibility <- d_to_summarise_assignment2 %>% {setNames(.$Twitter_Poster, if_else(.$Twitter_Poster>0, .$eligibility, ""))}
# ass_twlurker_eligibility <- d_to_summarise_assignment2 %>% {setNames(.$Twitter_Lurker, if_else(.$Twitter_Lurker>0, .$eligibility, ""))}
# 
# par(mfrow=c(1,4))
# ass_fbposter_eligibility %>% pie(main = "Assigned Facebook Posters",
#                                  col = ch3_colors_fbtwlposterlurker)
# ass_fblurker_eligibility %>% pie(main = "Assigned Facebook Lurkers",
#                                  col = ch3_colors_fbtwlposterlurker)
# ass_twposter_eligibility %>% pie(main = "Assigned Twitter Posters",
#                                  col = ch3_colors_fbtwlposterlurker)
# ass_twlurker_eligibility %>% pie(main = "Assigned Twitter Lurkers",
#                                  col = ch3_colors_fbtwlposterlurker)
```




```{r}
library(eulerr)

```




```{r}
raw_data %>%
  filter(DOV_ELIG_1==1) %>%
  transmute(assigned_fb_poster = DOV_ASSIGNED==1, elig_tw_poster = DOV_ELIG_3, elig_tw_lurker = DOV_ELIG_4) %>%
  #transmute(assigned, num_range("DOV_ELIG_", range = c(3,4))) %>%
  euler() %>% plot(., quantities = TRUE, fills = c(adjustcolor("gray", alpha = .5), ch3_colors_fbtwlposterlurker["tw_poster"], ch3_colors_fbtwlposterlurker["tw_lurker"]), edges = c(ch3_colors_fbtwlposterlurker["fb_poster"], NA, NA))

```



```{r}
#par(mfrow = c(1,4))

loss = "abs"

euler_size = 5

pdf("../results/euler_fbposter.pdf", width = euler_size, height = euler_size)
raw_data %>%
  filter(DOV_ELIG_1==1) %>% #filter for eligibility for current assignment
  transmute(assigned_fb_poster = DOV_ASSIGNED==1, elig_tw_poster = DOV_ELIG_3, elig_tw_lurker = DOV_ELIG_4) %>%
  #transmute(assigned, num_range("DOV_ELIG_", range = c(3,4))) %>%
  euler(loss = loss) %>% plot(., quantities = TRUE, fills = c(adjustcolor("gray", alpha = 0), ch3_colors_fbtwlposterlurker["tw_poster"], ch3_colors_fbtwlposterlurker["tw_lurker"]), edges = c(ch3_colors_fbtwlposterlurker["fb_poster"], NA, NA), legend = T)
dev.off()

pdf("../results/euler_fblurker.pdf", width = euler_size, height = euler_size)
raw_data %>%
  filter(DOV_ELIG_2==1) %>%
  transmute(assigned_fb_lurker = DOV_ASSIGNED==2, elig_tw_poster = DOV_ELIG_3, elig_tw_lurker = DOV_ELIG_4) %>%
  #transmute(assigned, num_range("DOV_ELIG_", range = c(3,4))) %>%
  euler(loss = loss) %>% plot(., quantities = TRUE, fills = c(adjustcolor("gray", alpha = 0), ch3_colors_fbtwlposterlurker["tw_poster"], ch3_colors_fbtwlposterlurker["tw_lurker"]), edges = c(ch3_colors_fbtwlposterlurker["fb_lurker"], NA, NA), legend = T)
dev.off()

pdf("../results/euler_twposter.pdf", width = euler_size, height = euler_size)
raw_data %>%
  filter(DOV_ELIG_3==1) %>%
  transmute(assigned_tw_poster = DOV_ASSIGNED==3, elig_fb_poster = DOV_ELIG_1, elig_fb_lurker = DOV_ELIG_2) %>%
  #transmute(assigned, num_range("DOV_ELIG_", range = c(3,4))) %>%
  euler(loss = loss) %>% plot(., quantities = TRUE, fills = c(adjustcolor("gray", alpha = 0), ch3_colors_fbtwlposterlurker["fb_poster"], ch3_colors_fbtwlposterlurker["fb_lurker"]), edges = c(ch3_colors_fbtwlposterlurker["tw_poster"], NA, NA), legend = T)
dev.off()

pdf("../results/euler_twlurker.pdf", width = euler_size, height = euler_size)
raw_data %>%
  filter(DOV_ELIG_4==1) %>%
  transmute(assigned_tw_lurker = DOV_ASSIGNED==4, elig_fb_poster = DOV_ELIG_1, elig_fb_lurker = DOV_ELIG_2) %>%
  #transmute(assigned, num_range("DOV_ELIG_", range = c(3,4))) %>%
  euler(loss = loss) %>% plot(., quantities = TRUE, fills = c(NA, ch3_colors_fbtwlposterlurker["fb_poster"], ch3_colors_fbtwlposterlurker["fb_lurker"]), edges = c(ch3_colors_fbtwlposterlurker["tw_lurker"], NA, NA), legend = T)
dev.off()


```


# Other Processing



## Check for NAs


```{r}
raw_data

```



```{r}
raw_data %>% filter(QUAL==1) %>% pull(PartyID7) %>% {mean(is.na(.))}
```




```{r}
all_colnames <- colnames(raw_data)
na_rate <- c()

for (i in 1:length(all_colnames)){
  na_rate[i] <- mean(is.na(raw_data[all_colnames[i]]))
}
names(na_rate) <- all_colnames

sort(na_rate, decreasing = T)

#na_rate[which(na_rate>.1)]
```


## Clean and Process the Data

```{r}
## Replace 98s with NA
#sa_num_raw
sa_num_raw[which(sa_num_raw == 98, arr.ind = T)] <- NA


rowmean_na <- (apply(sa_num_raw, MARGIN = 1, FUN = function(x){mean(is.na(x))}))
unique(rowmean_na)

any(rowmean_na == 1) #good
```


```{r}
# rearrange for phrase randomization
raw_data

randomized_phrases_randomization <- raw_data %>% select(starts_with("P_PHRASE_"))

phrases <- c("Black lives matter",
"abortion is healthcare",
"cis-gender",
"privilege",
"climate crisis",
"toxic masculinity",
"defund the police",
"equity",
"empathy",
"micro-aggression",
"safe space",
"POC",
"words matter",
"eat the rich",
"mansplain",
"heteronormative",
"voter suppression",
"all lives matter",
"sanctity of life",
"reverse racism",
"libtard",
"patriot",
"illegal alien",
"traditional values",
"blue lives matter",
"mainstream media",
"thug",
"do your own research",
"MAGA",
"free speech",
"cancel culture",
"personal responsibility",
"biological women",
"voter fraud")

randomized_phrases_indices <- data.frame(index = 7:40, phrase = phrases)

fixed_phrases_indices <- data.frame(index = 1:6, phrase = c("systemic racism", "big government", "human rights", "America first", "LatinX", "snowflake"))

```


```{r}
# create organized grid

sa_num <- matrix(NA, nrow = nrow(sa_num_raw), ncol = 40, dimnames = list(rows = raw_data$CaseId, cols = c(fixed_phrases_indices$phrase, randomized_phrases_indices$phrase)))

for (i in 1:6){
  sa_num[,i] <- sa_num_raw[,i]
}

#sa_num

#randomized_phrases_randomization

for (i in 1:nrow(randomized_phrases_randomization)){
  sa_num[i,unlist(randomized_phrases_randomization[i,])] <- sa_num_raw[i,7:20]
}

#sa_num

sa_num <- 4-sa_num
#saveRDS(sa_num, "tess_sa_num.rds")
```

```{r}

```



# Clean Rest of Survey

```{r}
raw_data$Q6A
```


DOV_ASSIGNED:
1 FB Poster
2 FB Lurker
3 TW Poster
4 TW Lurker

```{r}
data <- raw_data %>%
  select(-starts_with("P_PHRASE_")) %>%
  select(-starts_with("Q6")) %>%
  mutate(primary_platform = case_when(DOV_ASSIGNED %in% c(1,2) ~ "fb",
                                      DOV_ASSIGNED %in% c(3,4) ~ "tw"),
         poster = case_when(DOV_ASSIGNED %in% c(1,3) ~ TRUE,
                            DOV_ASSIGNED %in% c(2,4) ~ FALSE),
         platform_treatment = case_when(DOV_CONTEXT == 1 ~ 0,
                                        DOV_CONTEXT %in% c(2,3) ~ 1)) %>%
  mutate(relsim_fb = case_when(Q4 %in% 1:5 ~ Q4),
         relsim_tw = case_when(Q5 %in% 1:5 ~ Q5)) %>%
  dplyr::rename(acct_shows_name = Q7_1,
                acct_shows_face = Q7_2,
                acct_vis_rwf = Q7_3,
                acct_vis_fam = Q7_4,
                acct_vis_work = Q7_5)

data$IDEO[which(data$IDEO==-1)] <- NA
data$PartyID7[which(data$PartyID7==-1)] <- NA
data$GENDER[which(data$GENDER==0)] <- NA
data$AGE4[which(data$AGE4==99)] <- NA
data$AGE7[which(data$AGE7==99)] <- NA

data <- data %>% 
  mutate(male = (GENDER==1),
         poc = (RACETHNICITY!=1),
         college = (EDUC5>=4))

data

data$relsim <- NA
data$relsim[which(!is.na(data$relsim_fb))] <- data$relsim_fb[which(!is.na(data$relsim_fb))]
data$relsim[which(!is.na(data$relsim_tw))] <- data$relsim_fb[which(!is.na(data$relsim_tw))]


data$relsim_trin <- case_when(data$relsim < 3 ~ (-1),
                             data$relsim == 3 ~ (0),
                             data$relsim > 3 ~ (1))

hist(data$relsim_trin)

data <- data %>%
  mutate(age_dec = AGE/10)

#saveRDS(data, "tess_data.rds")
```


# Estimate Wordsticks

```{r}
indexer <- function(x,y){
  return(which(y == x))
}

prep_stan_data <- function(input, drop_na = TRUE){
  library(reshape)
  people <- unique(rownames(input))
  items <- unique(colnames(input)) %>% sort
  input_df <- as.data.frame(input) %>% mutate(id = rownames(input))
  input_melted <- melt(input_df, id.vars = "id") %>% mutate(variable=as.character(variable))
  if(drop_na==TRUE){input_melted <- input_melted %>% drop_na()}
  input_melted <- input_melted %>% mutate(person_index = NA,item_index = NA)
  for (i in 1:nrow(input_melted)) {
    input_melted$person_index[i] <- indexer(input_melted$id[i], people)
    input_melted$item_index[i] <- indexer(input_melted$variable[i], items)
  }
  return(input_melted)
}
```


```{r}
# 4 point estimation prep
sa_4point <- sa_num

melted <- prep_stan_data(sa_4point)
person_metadata <- data %>% mutate(person_index = 1:nrow(.))
melted <- left_join(melted, person_metadata)

melted$value <- melted$value + 1

#set up initial values
statements <- colnames(sa_4point)
statements_tomatch <- tolower(statements)

sa_sdi_cor <- apply(sa_4point, MARGIN = 2, FUN = function(x) return(cor(x, person_metadata$IDEO, use = "complete.obs")))

sa_colmeans <- sa_4point %>% colMeans(na.rm = T) %>% scale %>% as.vector
hist(sa_colmeans)

sa_rowmeans <- sa_4point %>% rowMeans(na.rm = T) %>% scale %>% as.vector
hist(sa_rowmeans)
any(is.na(sa_rowmeans))

scaled_ideology <- person_metadata$IDEO %>% scale %>% as.vector
hist(scaled_ideology)

scaled_ideology[which(is.na(scaled_ideology))] <- 0

if (run_stan) {
  init_1 <- function(chain_id) {
    list(gamma = sa_sdi_cor,
         beta = sa_rowmeans,
         alpha_raw = scaled_ideology)
  }
  
  
  stan_dat <- list(say = melted$value,
                   subj = melted$person_index,
                   item = melted$item_index,
                   J = nlevels(as.factor(melted$person_index)),
                   K = nlevels(as.factor(melted$item_index)),
                   N = nrow(melted),
                   fixright = which(colnames(sa_4point) == "America first"))
  
  chains = 4
  stan_iter = 2500
  options(mc.cores = chains)
  stan_fit <- stan("wordsticks.stan",
                       data = stan_dat,
                       init = init_1,
                       chains = chains, iter = stan_iter)
  saveRDS(stan_fit, "../results/wordsticks_fit.rds")
} else {
  stan_fit <- readRDS("../results/wordsticks_fit.rds")
}

```


```{r}
alpha_samples <- rstan::extract(stan_fit, pars = c("alpha"), permuted=T, inc_warmup = F)$alpha %>% t
beta_samples <- rstan::extract(stan_fit, pars = c("beta"), permuted=T, inc_warmup = F)$beta %>% t

```


```{r}
d_final <- data %>% mutate(alpha = apply(alpha_samples, MARGIN = 1, FUN = median), beta = apply(beta_samples, MARGIN = 1, FUN = median))
d_final #use for treatment effects, benchmarking

```

## Prep Data for Stickplots


```{r}
#alpha_samples <- rstan::extract(stan_fit, pars = c("alpha"), permuted=T, inc_warmup = F)$alpha %>% t

phrase_index <- melted %>% distinct(item_index, .keep_all = T) %>% arrange(item_index) %>% pull(variable)

#alpha_samples <- rstan::extract(stan_fit, pars = c("alpha"), permuted=T, inc_warmup = F)$alpha %>% t
#beta_samples <- rstan::extract(stan_fit, pars = c("beta"), permuted=T, inc_warmup = F)$beta %>% t
gamma_samples <- rstan::extract(stan_fit, pars = c("gamma"), permuted=T, inc_warmup = F)$gamma %>% t

rownames(gamma_samples) <- phrase_index
#d3_A_samples <- rstan::extract(stan_fit, pars = c("d3_A"), permuted=T, inc_warmup = F)$d3_A %>% t
#rownames(d3_A_samples) <- phrase_index_3point
#d3_B_samples <- rstan::extract(stan_fit, pars = c("d3_B"), permuted=T, inc_warmup = F)$d3_B %>% t
#rownames(d3_B_samples) <- phrase_index_3point
d4_A_samples <- rstan::extract(stan_fit, pars = c("d4_A"), permuted=T, inc_warmup = F)$d4_A %>% t
rownames(d4_A_samples) <- phrase_index
d4_B_samples <- rstan::extract(stan_fit, pars = c("d4_B"), permuted=T, inc_warmup = F)$d4_B %>% t
rownames(d4_B_samples) <- phrase_index
d4_C_samples <- rstan::extract(stan_fit, pars = c("d4_C"), permuted=T, inc_warmup = F)$d4_C %>% t
rownames(d4_C_samples) <- phrase_index

#ct3_1_samples <- rstan::extract(stan_fit, pars = c("c3_transformed_1"), permuted=T, inc_warmup = F)$c3_transformed_1 %>% t
#ct3_2_samples <- rstan::extract(stan_fit, pars = c("c3_transformed_2"), permuted=T, inc_warmup = F)$c3_transformed_2 %>% t
#rownames(ct3_1_samples) <- phrase_index_3point
#rownames(ct3_2_samples) <- phrase_index_3point

ct4_1_samples <- rstan::extract(stan_fit, pars = c("c4_transformed_1"), permuted=T, inc_warmup = F)$c4_transformed_1 %>% t
ct4_2_samples <- rstan::extract(stan_fit, pars = c("c4_transformed_2"), permuted=T, inc_warmup = F)$c4_transformed_2 %>% t
ct4_3_samples <- rstan::extract(stan_fit, pars = c("c4_transformed_3"), permuted=T, inc_warmup = F)$c4_transformed_3 %>% t
rownames(ct4_1_samples) <- phrase_index
rownames(ct4_2_samples) <- phrase_index
rownames(ct4_3_samples) <- phrase_index
```


```{r}

pooled_item_gammas <- gamma_samples %>% apply(., MARGIN = 1, FUN = quantile, probs = c(0.025, 0.5, 0.975)) %>% t() %>% as.data.frame() %>% dplyr::rename("lower" = "2.5%", "median" = "50%", "upper" = "97.5%")
```


```{r}
# 4-point scale cutpoints
cutpoints_transformed_df_4point <- data.frame(no_modeled = ct4_1_samples %>% apply(., MARGIN = 1, FUN = median),
                                              middle_modeled = ct4_2_samples %>% apply(., MARGIN = 1, FUN = median),
                                              yes_modeled = ct4_3_samples %>% apply(., MARGIN = 1, FUN = median))
cutpoints_transformed_df_4point$gammas <- pooled_item_gammas$median[match(rownames(cutpoints_transformed_df_4point), rownames(pooled_item_gammas))]
cutpoints_transformed_df_4point$gammas_upper <- pooled_item_gammas$upper[match(rownames(cutpoints_transformed_df_4point), rownames(pooled_item_gammas))]
cutpoints_transformed_df_4point$gammas_lower <- pooled_item_gammas$lower[match(rownames(cutpoints_transformed_df_4point), rownames(pooled_item_gammas))]

#cutpoints_transformed_df_4point
```


```{r}
## -----------------------------------------------------------------------------
message("Plotting gammas...")

gammas_toplot <- pooled_item_gammas %>% arrange((median))

gamma_xlim = 6
gamma_sidemar = 4

pdf(file = paste0("../results/gammas.pdf"), width = 6, height = 14)

par(bty="n", xpd = T, mar = c(5.1, gamma_sidemar, 3.1, gamma_sidemar))
plot(gammas_toplot$median, 1:nrow(gammas_toplot), ylab = "", yaxt = "n", xlab = expression(paste("Phrase Slants ", gamma)), xlim = c(-gamma_xlim,gamma_xlim), main = "Item Gammas")
points(gammas_toplot$median, 1:nrow(gammas_toplot), pch=16)
segments(x0 = gammas_toplot$lower, x1 = gammas_toplot$upper, y0 = 1:nrow(gammas_toplot), col = rgb(0,0,0,.5))
text(x = if_else(gammas_toplot$median<0, gammas_toplot$lower,gammas_toplot$upper), y = 1:nrow(gammas_toplot), labels = rownames(gammas_toplot), pos = if_else(gammas_toplot$median<0, 2,4))
par(xpd=F)
abline(v=0, lty=3)

dev.off()

```


```{r}
# Set stickplot color scheme

value = .8
saturation = .7

lo_hi_colorspread <- 20

no_color_hsv = hsv(0/365, saturation, value)
maybe_lo_hsv = hsv((52-lo_hi_colorspread)/365, saturation, value)
maybe_color_hsv = hsv(52/365, saturation, value)
maybe_hi_hsv = hsv((52+lo_hi_colorspread)/365, saturation, value)
yes_color_hsv = hsv(136/365, saturation, value)

```


```{r}
base_rug_resolution = 2000
#base_rug_bandwidth = 2000

#get alpha samples (same as before)
alpha_samples_unlisted <- alpha_samples %>% c() %>% sample (100000)

# rescale range of alpha_samples_unlisted so that value domain matches plot domain
alpha_samples_unlisted_rescaled <- (alpha_samples_unlisted/4)*base_rug_resolution/2
alpha_samples_unlisted_rescaled_rounded <- round(alpha_samples_unlisted_rescaled)

# plot in 3-pixel bandwidth
alpha_samples_unlisted_rescaled_rounded <- c(alpha_samples_unlisted_rescaled_rounded, alpha_samples_unlisted_rescaled_rounded+1, alpha_samples_unlisted_rescaled_rounded-1)

# make counts
vec_factor <- factor(alpha_samples_unlisted_rescaled_rounded, levels = -(base_rug_resolution/2):(base_rug_resolution/2))
counts <- as.integer(table(vec_factor))
counts_normalized <- (1 - counts/max(counts))

# make 3d array
array_3d <- array(0, dim = c(length(counts_normalized), 3, 40))

# Fill each slice of the new dimensions with the 'counts' vector
for (i in 1:dim(array_3d)[2]) {
  for (j in 1:dim(array_3d)[3]) {
    array_3d[, i, j] <- counts_normalized
  }
}

# reshape array to work as raster
rug_raster <- array_3d %>% aperm(., c(3,1,2))
```


```{r}
maybe_color_rgb <- maybe_color_hsv %>% col2rgb
no_color_rgb <- no_color_hsv %>% col2rgb
yes_color_rgb <- yes_color_hsv %>% col2rgb

maybe_hi_rgb <- maybe_hi_hsv %>% col2rgb
maybe_lo_rgb <- maybe_lo_hsv %>% col2rgb

```


```{r}
draw_sticks_baseR <- function(img, x0, x1, color) {
  x0 <- max(min(x0, dim(img)[1]), 1)
  x1 <- max(min(x1, dim(img)[1]), 1)
  if (x0 > x1) { temp <- x0; x0 <- x1; x1 <- temp }
  img[x0:x1, 1, ] <- array(rep(color, each=length(x1:x0)), dim = c(length(x1:x0), 1, 3))
  return(img)
}

map_range <- function(x, from_min, from_max, to_min, to_max) {
  (x - from_min) * (to_max - to_min) / (from_max - from_min) + to_min
}


clean_stick_rasters <- function(input){
  output <- input %>% as.array %>% aperm(., c(2,1,3)) %>% {./255}
  output[which(is.na(output), arr.ind = T)] <- 1
  return(output)
}

```


```{r}
## ----graphics settings--------------------------------------------------------
# plot settings
plot_scale = .83

fullpage_width = 12*plot_scale
halfpage_width = 6*plot_scale

square_plot_size = 5*plot_scale

phraselevel_effects_height = 6*plot_scale

#squareplots settings
squareplot_top_margin <- 0

#sbs settings
sbs_side_padding <- 14*plot_scale
sbs_inner_padding <- 1*plot_scale
sbs_pdf_height = halfpage_width
sbs_statement_cex <- .9
sbs_phrase_font <- 2

limits <- c(-6.03169, 6.03169)

stick_xlim <- 4
stick_width_padding <- 1
stick_width <- stick_xlim + stick_width_padding

statement_offset <- 1
main_lwd <- 8
bar_height = .8

# Termlevel treateffects
font_phraselevel_treateffects <- 2

###

# Parameters
width_px <- 2000
height_px <- 40
inner_height_px <- 1
start_iter <- 1
#N <- ncol(ct3_1_samples)
N <- 2500

```


```{r}
# 4-point phrases

#J <- length(phrase_index_4point)
J <- nrow(ct4_1_samples)

# Initialize list to store averaged images
stacked_images <- vector("list", J)

# Iterate over columns
pb <- progress_bar$new(total = N, format = "  Plotting [:bar] :percent eta: :eta")
for (i in start_iter:N) {
  pb$tick()
  cutpoints_transformed_df_iterate <- data.frame(
    no_modeled = ct4_1_samples[, i],
    middle_modeled = ct4_2_samples[,i],
    yes_modeled = ct4_3_samples[, i]
  )
  for (j in 1:J) {
    png_data <- array(NA, dim = c(width_px, inner_height_px, 3))
    png_data = draw_sticks_baseR(
      png_data,
      x0 = cutpoints_transformed_df_iterate$no_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      x1 = cutpoints_transformed_df_iterate$middle_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      color = maybe_lo_rgb
    )
    png_data = draw_sticks_baseR(
      png_data,
      x0 = cutpoints_transformed_df_iterate$middle_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      x1 = cutpoints_transformed_df_iterate$yes_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      color = maybe_hi_rgb
    )
    png_data = draw_sticks_baseR(
      png_data,
      x0 = cutpoints_transformed_df_iterate$no_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      x1 = if_else(
        sign(cutpoints_transformed_df_iterate$yes_modeled[j] - cutpoints_transformed_df_iterate$no_modeled[j]) == 1,
        limits[1], limits[2]
      ) %>% map_range(., -stick_width, stick_width, 0, width_px),
      color = no_color_rgb
    )
    png_data = draw_sticks_baseR(
      png_data,
      x0 = cutpoints_transformed_df_iterate$yes_modeled[j] %>% map_range(., -stick_width, stick_width, 0, width_px),
      x1 = if_else(
        sign(cutpoints_transformed_df_iterate$yes_modeled[j] - cutpoints_transformed_df_iterate$no_modeled[j]) == -1,
        limits[1], limits[2]
      ) %>% map_range(., -stick_width, stick_width, 0, width_px),
      color = yes_color_rgb
    )
    if (i == 1) {
      stacked_images[[j]] <- png_data
    } else {
      stacked_images[[j]] <- stacked_images[[j]] + png_data
    }
  }
}

averaged_images <- lapply(stacked_images, function(img) img / N)

resized_images_4point <- lapply(averaged_images, clean_stick_rasters)


```


```{r}
## -----------------------------------------------------------------------------
rugtop = .4

```



```{r}
# sbs smooth 4point ALL
par(family = "SourceSansPro-Regular")
pdf(file = paste0("../results/sbs_smooth_all_4point.pdf"), width = fullpage_width, height = sbs_pdf_height)
par(mfrow=c(1,2))

#left
cutpoints_transformed_df_toplot <- cutpoints_transformed_df_4point %>%
  arrange(desc(middle_modeled)) %>%
  filter(gammas<0)

xlim <- c(-stick_xlim,stick_xlim)
x_stickwidth <- c(-stick_width,stick_width)
bar_ys <- (1:nrow(cutpoints_transformed_df_toplot))
ylim <- c(0, max(bar_ys))

limits <- c(-max(abs(cutpoints_transformed_df_toplot)+1),max(abs(cutpoints_transformed_df_toplot)+1))

par(mar = c(5.1, sbs_side_padding, 3.1, sbs_inner_padding), bty = "n")
plot(cutpoints_transformed_df_toplot$no_modeled, bar_ys, ylab = "", yaxt = "n", xlab = "Respondent Lexical Ideology", xlim = xlim, ylim = ylim, type = "n", main = "", xaxt = "n")
title(main="Left-Slanted Phrases", line=0)

par(xpd=F)

for (j in 1:nrow(cutpoints_transformed_df_toplot)){
  rasterImage(resized_images_4point[[which(phrase_index==rownames(cutpoints_transformed_df_toplot)[j])]], xleft = x_stickwidth[1], xright = x_stickwidth[2], ybottom = bar_ys[j]-bar_height/2, ytop = bar_ys[j]+bar_height/2)
}

par(xpd=T)
text(if_else(sign(cutpoints_transformed_df_toplot$yes_modeled - cutpoints_transformed_df_toplot$no_modeled)==1, xlim[2], xlim[1]), bar_ys, bar_ys,      labels = rownames(cutpoints_transformed_df_toplot) %>% toupper,      cex = sbs_statement_cex,
     pos = if_else(sign(cutpoints_transformed_df_toplot$yes_modeled - cutpoints_transformed_df_toplot$no_modeled)==1, 4, 2),
     font = sbs_phrase_font,      offset = statement_offset)

par(xpd=F)
rasterImage(rug_raster, xleft = xlim[1], xright = xlim[2], ybottom = -1, ytop = rugtop)

axis(side = 1)

# right
cutpoints_transformed_df_toplot <- cutpoints_transformed_df_4point %>%
  arrange((middle_modeled)) %>%
  filter(gammas>0)

bar_ys <- (1:nrow(cutpoints_transformed_df_toplot))
ylim <- c(0, max(bar_ys))

limits <- c(-max(abs(cutpoints_transformed_df_toplot)+1),max(abs(cutpoints_transformed_df_toplot)+1))

par(mar = c(5.1, sbs_inner_padding, 3.1, sbs_side_padding), bty = "n")
plot(cutpoints_transformed_df_toplot$no_modeled, bar_ys, ylab = "", yaxt = "n", xlab = "Respondent Lexical Ideology", xlim = xlim, ylim = ylim, type = "n", main = "", xaxt = "n")
title(main="Right-Slanted Phrases", line=0)

par(xpd=F)

for (j in 1:nrow(cutpoints_transformed_df_toplot)){
  rasterImage(resized_images_4point[[which(phrase_index==rownames(cutpoints_transformed_df_toplot)[j])]], xleft = x_stickwidth[1], xright = x_stickwidth[2], ybottom = bar_ys[j]-bar_height/2, ytop = bar_ys[j]+bar_height/2)
}



par(xpd=T)
text(if_else(sign(cutpoints_transformed_df_toplot$yes_modeled - cutpoints_transformed_df_toplot$no_modeled)==1, xlim[2], xlim[1]), bar_ys, bar_ys,      labels = rownames(cutpoints_transformed_df_toplot) %>% toupper,      cex = sbs_statement_cex,
     pos = if_else(sign(cutpoints_transformed_df_toplot$yes_modeled - cutpoints_transformed_df_toplot$no_modeled)==1, 4, 2),
     font = sbs_phrase_font,      offset = statement_offset)

par(xpd=F)
rasterImage(rug_raster, xleft = xlim[1], xright = xlim[2], ybottom = -1, ytop = rugtop)

axis(side = 1)
#par(xpd=T)
#legend(x=-5, y=20, legend = c("Definitely", "Probably", "Probably Not", "Definitely Not"), pch = 15, cex=.8, col = c(yes_color_hsv, maybe_hi_hsv, maybe_lo_hsv, no_color_hsv), bty = "o", horiz = T)
dev.off()

```


```{r}
pdf(file = paste0("../results/sbs_legend.pdf"), width = fullpage_width, height = sbs_pdf_height/10)
par(xpd=T, mar = c(0,0,0,0), bty="n")
plot(x = c(0,1), y = c(0,1), type = "n", xaxt = "n", yaxt = "n")
legend("center", legend = c("Definitely", "Probably", "Probably Not", "Definitely Not"), pch = 15, cex=.8, col = c(yes_color_hsv, maybe_hi_hsv, maybe_lo_hsv, no_color_hsv), bty = "o", horiz = T, text.width=.1, pt.cex = 1.25)
dev.off()

```








# Hypothesis Tests

## H1


```{r}
estimatr::lm_robust(beta ~ platform_treatment, data = d_final %>% filter(poster), se_type = "HC2") %>% coefplot::coefplot()

mod_h1_pooled_ks <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
#mod_h1

(mod_h1_pooled_ks$p.value['platform_treatment']/2) < .00001

if ((mod_h1_pooled_ks$p.value['platform_treatment']/2) < .00001){
  writeLines("($p<.00001$, pre-registered one-sided test),", "../results/h1_p.txt")
}
```


## H2

```{r}
estimatr::lm_robust(alpha ~ platform_treatment, data = d_final %>% filter(poster), se_type = "HC2") %>% coefplot::coefplot()

mod_h2_pooled_ks <- estimatr::lm_robust(alpha ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
#mod_h2

(mod_h2_pooled_ks$p.value['platform_treatment']/2) < .05 #p=.36

h2_p_rounded <- round(mod_h2_pooled_ks$p.value['platform_treatment']/2, 2) %>% as.character() %>% substring(., first = 2)

writeLines(paste0("$p\\approx",h2_p_rounded,"$, pre-registered one-sided test),"), "../results/h2_p.txt")

```


## H3

```{r}
sig_thresholds <- c(.1, .01, .001, .0001, .00001, .000001, .0000001, .00000001)

```


```{r}
test_h3 <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater")
#test_h3

test_h3$p.value < 0.000001 #p=3e-07

#test_h3$statistic %>% round(2) %>% paste0("F=",.,",") %>% writeLines(., "../results/h3_fstat.txt")

paste0("($F=",test_h3$statistic %>% round(2),"$, $p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h3$p.value)]),"}$, pre-registered one-sided test).") %>% writeLines(., "../results/h3_fp.txt")


```


```{r}
# plot colors
color_poster_online = rgb(.8,.2,.8,1)
color_poster_offline = rgb(.2,.8,.2,1)
color_lurker = rgb(.8,.1,.2,1)

```



```{r}
# color_poster = rgb(.2,.8,.2,1)
# color_lurker = rgb(.8,.1,.2,1)

this_bw = .25

# Compute histograms
density_poster <- density(d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), bw = this_bw)
density_lurker <- density(d_final %>% filter(!poster) %>% filter(platform_treatment==0) %>% pull(alpha), bw = this_bw)

# Plot and fill the first density
plot(density_poster, main="Overlaying Two Filled Densities", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster$x, density_poster$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
lines(density_poster, col=color_poster_offline, lwd=2)
polygon(density_lurker$x, density_lurker$y, col=adjustcolor(color_lurker, alpha.f=0.5), border=NA)
lines(density_lurker, col=color_lurker, lwd=2)
legend("topright", legend = c("Lurkers Offline", "Posters Offline"), col = c(color_lurker, color_poster_offline), pch = 15, bty = "n")


```



## H4

```{r}
test_h4 <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater")
test_h4

test_h4$p.value
test_h4$p.value < .05 # Null for H4, as predicted!

paste0("($F=",test_h4$statistic %>% round(2),"$, $p = ", test_h4$p.value %>% round(.,2),"}$, pre-registered one-sided test).") %>% writeLines(., "../results/h4_fp.txt")
```


```{r}
# color_poster_online = rgb(.8,.2,.8,1)
# color_poster_offline = rgb(.2,.8,.2,1)

this_bw = .25

# Compute histograms
density_poster_online <- density(d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha), bw = this_bw)
density_poster_offline <- density(d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), bw = this_bw)

par(bty = "n")

# Plot and fill the first density
plot(density_poster_online, main="Overlaying Two Filled Densities", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster_offline$x, density_poster_offline$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
lines(density_poster_offline, col=color_poster_offline, lwd=2)
polygon(density_poster_online$x, density_poster_online$y, col=adjustcolor(color_poster_online, alpha.f=0.5), border=NA)
lines(density_poster_online, col=color_poster_online, lwd=2)
legend("topright", legend = c("Posters Online", "Posters Offline"), col = c(color_poster_online, color_poster_offline), pch = 15, bty = "n")


```

# Exploratory Analyses

## H1 Het Fx on Beta by Alpha

```{r}
poster_alpha_quartiles <- d_final %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.25,.5,.75))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[3]), se_type = "HC2")

test_mod_1$coefficients["platform_treatment"]
test_mod_2$coefficients["platform_treatment"]
test_mod_3$coefficients["platform_treatment"]
test_mod_4$coefficients["platform_treatment"]



```


```{r}
data_to_plot <- d_final %>% filter(poster)# %>% filter(relsim_trin)

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.2,.4,.6,.8))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")


plot(x = c(-2,.5), y = c(1,5), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5))
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)
)

```




```{r}
y_adj <- .2


data_to_plot <- d_final %>% filter(poster)
mark_col = "gray1"

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.2,.4,.6,.8))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,6), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)-y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```



```{r}
y_adj <- .2


data_to_plot <- d_final %>% filter(poster)
mark_col = "gray1"

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.33333,.66666))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,4), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)-y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```


```{r}
d_toplot <- d_final %>% filter(!is.na(IDEO)) %>% filter(!is.na(relsim))# %>% group_by(IDEO) %>% summarise(mean_relsim = mean(relsim))

plot(d_toplot$IDEO, d_toplot$relsim)

range(d_final$relsim, na.rm = T)


# Sample data
df <- d_toplot

# Tabulate by IDEO and relsim
tabulated <- table(df$IDEO, df$relsim)

# Transpose the table
transposed <- t(tabulated)

# Create the stacked bar chart
barplot(transposed, beside=FALSE, col=rainbow(5),
        legend.text=rownames(transposed), ylim=c(0, max(rowSums(transposed)) + 5),
        xlab="IDEO", ylab="Count", main="Stacked Bar Chart of IDEO by relsim")

# Normalize counts to get proportions
proportions <- sweep(tabulated, 1, rowSums(tabulated), FUN = "/")

# Transpose the table of proportions
transposed_proportions <- t(proportions)

# Create the stacked bar chart showing proportions
barplot(transposed_proportions, beside=FALSE, col=rainbow(5),
        legend.text=rownames(transposed_proportions), ylim=c(0, 1),
        xlab="IDEO", ylab="Proportion", main="Stacked Bar Chart of IDEO by relsim (Proportion)")

```




```{r}
#with interaction

y_adj <- .2


data_to_plot <- d_final %>% filter(poster)
mark_col = "gray1"

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.33333,.66666))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,4), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)-y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```


```{r}
y_adj <- .2

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.33333,.66666))

data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="fb")
mark_col = "purple3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,4), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)-y_adj, col = mark_col
)


data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="tw")
mark_col = "skyblue3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)+y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```



```{r}
#by platform, with interaction effect
y_adj <- .2

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.33333,.66666))

data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="fb")
mark_col = "purple3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,4), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)-y_adj, col = mark_col
)


data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="tw")
mark_col = "skyblue3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)+y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```







```{r}
y_adj <- .2

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.33333,.66666))

data_to_plot <- d_final %>% filter(poster) %>% filter(relsim_trin==-1)
mark_col = "red4"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,4), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)-y_adj, col = mark_col
)


data_to_plot <- d_final %>% filter(poster) %>% filter(relsim_trin==0)
mark_col = "gold4"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3), col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3), col = mark_col
)

data_to_plot <- d_final %>% filter(poster) %>% filter(relsim_trin==1)
mark_col = "green4"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[2]), se_type = "HC2")


points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"]),
       y = c(1:3)+y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"]
                ), y0 = c(1:3)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```




```{r}
y_adj <- .25


data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="fb")
mark_col = "red3"

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.2,.4,.6,.8))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,6), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)-y_adj, col = mark_col)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)-y_adj, col = mark_col
)

data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="tw")
mark_col = "forestgreen"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")

points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)+y_adj, col = mark_col)

segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```



```{r}
y_adj <- .25


data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="fb")
mark_col = "red3"

poster_alpha_quartiles <- data_to_plot %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.2,.4,.6,.8))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")


plot(x = c(-1.5,1.5), y = c(0,6), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)-y_adj, col = mark_col)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)-y_adj, col = mark_col
)

data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="tw")
mark_col = "forestgreen"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[4]), se_type = "HC2")

points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)+y_adj, col = mark_col)

segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```





```{r}
y_adj <- .2


data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="fb")
mark_col = "purple3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==1), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==2), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==3), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==4), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==5), se_type = "HC2")

plot(x = c(-1.5,1.5), y = c(0,6), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)-y_adj, col = mark_col
)

data_to_plot <- d_final %>% filter(poster) %>% filter(primary_platform=="tw")
mark_col = "skyblue3"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==1), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==2), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==3), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==4), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==5), se_type = "HC2")

points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)+y_adj, col = mark_col, pch = 16)

segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)+y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```





```{r}
y_adj <- .2


data_to_plot <- d_final %>% filter(poster)# %>% filter(primary_platform=="fb")
mark_col = "gray1"

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==1), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==2), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==3), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==4), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + college + poc, data = data_to_plot %>% filter(poster) %>% filter(IDEO==5), se_type = "HC2")

plot(x = c(-1.5,1.5), y = c(0,6), type = "n")
points(x = c(test_mod_1$coefficients["platform_treatment"],
             test_mod_2$coefficients["platform_treatment"],
             test_mod_3$coefficients["platform_treatment"],
             test_mod_4$coefficients["platform_treatment"],
             test_mod_5$coefficients["platform_treatment"]),
       y = c(1:5)-y_adj, col = mark_col, pch = 16)
segments(x0 = c(test_mod_1$conf.low["platform_treatment"],
                test_mod_2$conf.low["platform_treatment"],
                test_mod_3$conf.low["platform_treatment"],
                test_mod_4$conf.low["platform_treatment"],
                test_mod_5$conf.low["platform_treatment"]),
         x1 = c(test_mod_1$conf.high["platform_treatment"],
                test_mod_2$conf.high["platform_treatment"],
                test_mod_3$conf.high["platform_treatment"],
                test_mod_4$conf.high["platform_treatment"],
                test_mod_5$conf.high["platform_treatment"]), y0 = c(1:5)-y_adj, col = mark_col
)

abline(v = 0, lty = 3)

```







```{r}
poster_alpha_quartiles <- d_final %>% filter(poster) %>% pull(alpha) %>% quantile(., c(.1,.2,.3,.4,.5,.6,.7,.8,.9))

test_mod_1 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha<poster_alpha_quartiles[1]), se_type = "HC2")
test_mod_2 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[1]) %>% filter(alpha<poster_alpha_quartiles[2]), se_type = "HC2")
test_mod_3 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[2]) %>% filter(alpha<poster_alpha_quartiles[3]), se_type = "HC2")
test_mod_4 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[3]) %>% filter(alpha<poster_alpha_quartiles[4]), se_type = "HC2")
test_mod_5 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[4]) %>% filter(alpha<poster_alpha_quartiles[5]), se_type = "HC2")
test_mod_6 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[5]) %>% filter(alpha<poster_alpha_quartiles[6]), se_type = "HC2")
test_mod_7 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[6]) %>% filter(alpha<poster_alpha_quartiles[7]), se_type = "HC2")
test_mod_8 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[7]) %>% filter(alpha<poster_alpha_quartiles[8]), se_type = "HC2")
test_mod_9 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>=poster_alpha_quartiles[8]) %>% filter(alpha<poster_alpha_quartiles[9]), se_type = "HC2")
test_mod_10 <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(alpha>poster_alpha_quartiles[9]), se_type = "HC2")

test_mod_1$coefficients["platform_treatment"]
test_mod_2$coefficients["platform_treatment"]
test_mod_3$coefficients["platform_treatment"]
test_mod_4$coefficients["platform_treatment"]
test_mod_5$coefficients["platform_treatment"]
test_mod_6$coefficients["platform_treatment"]
test_mod_7$coefficients["platform_treatment"]
test_mod_8$coefficients["platform_treatment"]
test_mod_9$coefficients["platform_treatment"]
test_mod_10$coefficients["platform_treatment"]
```



## Interaction with Likemindedness

### Likemindedness

```{r}
plot(d_final %>% filter(poster) %>% pull(IDEO), d_final %>% filter(poster) %>% pull(relsim))

boxplot(relsim ~ IDEO, data = d_final %>% filter(poster))

d_relsim_by_ideo <- d_final %>% filter(poster) %>% group_by(IDEO) %>% summarise(mean_relsim = mean(relsim, na.rm = T)) %>% filter(!is.na(IDEO))

plot(d_relsim_by_ideo$IDEO, d_relsim_by_ideo$mean_relsim)

d_final$relsim_trin

d_final %>% filter(poster) %>% pull(IDEO) %>% hist

d_final %>% filter(poster) %>% filter(IDEO==1) %>% pull(relsim) %>% hist
d_final %>% filter(poster) %>% filter(IDEO==2) %>% pull(relsim) %>% hist
d_final %>% filter(poster) %>% filter(IDEO==3) %>% pull(relsim) %>% hist
d_final %>% filter(poster) %>% filter(IDEO==4) %>% pull(relsim) %>% hist
d_final %>% filter(poster) %>% filter(IDEO==5) %>% pull(relsim) %>% hist

```


### H1


```{r}
#DV: beta
mod_h1_int_relsim_adj <- estimatr::lm_robust(beta ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
mod_h1_int_relsim_adj$coefficients["platform_treatment:relsim"]
mod_h1_int_relsim_adj$p.value["platform_treatment:relsim"] < .05

#mod_h1_int_relsim_trin_adj <- estimatr::lm_robust(beta ~ platform_treatment*relsim_trin + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")

# unadjusted: 
mod_h1_int_relsim_unadj <- estimatr::lm_robust(beta ~ platform_treatment*relsim, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03
mod_h1_int_relsim_unadj$coefficients["platform_treatment:relsim"]
mod_h1_int_relsim_unadj$p.value["platform_treatment:relsim"] < .05

#mod_h1_int_relsim_trin_adj <- estimatr::lm_robust(beta ~ platform_treatment*relsim_trin, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03

```


```{r}
#DV: beta (subset analyses, 3-level)

#adjusted model
mod_h1_sub_relsim_trin_lo_adj <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(relsim_trin<0), se_type = "HC2")
mod_h1_sub_relsim_trin_lo_adj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_lo_adj$p.value["platform_treatment"]/2 < .00001 # p=.0000086

mod_h1_sub_relsim_trin_0_adj <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(relsim_trin==0), se_type = "HC2")
mod_h1_sub_relsim_trin_0_adj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_0_adj$p.value["platform_treatment"]/2 < .05 #p=.01

mod_h1_sub_relsim_trin_hi_adj <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(relsim_trin>0), se_type = "HC2")
mod_h1_sub_relsim_trin_hi_adj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_hi_adj$p.value["platform_treatment"]/2 < .05 #p=.40


# unadjusted models --- 
mod_h1_sub_relsim_trin_lo_unadj <- estimatr::lm_robust(beta ~ platform_treatment, data = d_final %>% filter(poster) %>% filter(relsim_trin<0), se_type = "HC2") #-.4, p<.0001
mod_h1_sub_relsim_trin_lo_unadj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_lo_unadj$p.value["platform_treatment"]/2 < .05

mod_h1_sub_relsim_trin_0_unadj <- estimatr::lm_robust(beta ~ platform_treatment, data = d_final %>% filter(poster) %>% filter(relsim_trin==0), se_type = "HC2") #-.27, p<.05
mod_h1_sub_relsim_trin_0_unadj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_0_unadj$p.value["platform_treatment"]/2 < .05

mod_h1_sub_relsim_trin_hi_unadj <- estimatr::lm_robust(beta ~ platform_treatment, data = d_final %>% filter(poster) %>% filter(relsim_trin>0), se_type = "HC2") #.06, p=.73
mod_h1_sub_relsim_trin_hi_unadj$coefficients["platform_treatment"]
mod_h1_sub_relsim_trin_hi_unadj$p.value["platform_treatment"]/2 < .05


```


### H2

```{r}
#DV: alpha
mod_h2_int_relsim_adj <- estimatr::lm_robust(alpha ~ platform_treatment*relsim + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
mod_h2_int_relsim_trin_adj <- estimatr::lm_robust(alpha ~ platform_treatment*relsim_trin + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")

# unadjusted: 
mod_h2_int_relsim_unadj <- estimatr::lm_robust(alpha ~ platform_treatment*relsim, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03
mod_h2_int_relsim_trin_unadj <- estimatr::lm_robust(alpha ~ platform_treatment*relsim_trin, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03

```


### H3

```{r}
# H3 -- self-selection
# main H confirmed for relsim_trin<=0

# Amongst people for whom offline is more likeminded than online, posters are more extreme than lurkers
test_h3_sub_relsim_trin_lo <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin<0) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(relsim_trin<0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #1.60; p<.001

# Amongst people for whom offline and online are equally likeminded, posters are more extreme than lurkers
test_h3_sub_relsim_trin_0 <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin==0) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(relsim_trin==0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #1.47; p<.01

# Amongst people for whom online is more likeminded than offline, the difference is not significant at conventional levels
test_h3_sub_relsim_trin_hi <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin>0) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(relsim_trin>0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #1.39; p = .15


# synthesis: self-selection aligns with extremity MOST among people whose online networks are LESS likeminded than their offline networks --> this makes sense, if people self-censor online when online is non-likeminded and their speech is moderate
```

### H4

```{r}
# H4 -- polarization
# main H (null) confirmed

test_h4_sub_relsim_trin_lo <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin<0) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(relsim_trin<0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #.98, p=.60

test_h4_sub_relsim_trin_0 <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin==0) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(relsim_trin==0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #.88, p=.88

test_h4_sub_relsim_trin_hi <- var.test(d_final %>% filter(poster) %>% filter(relsim_trin>0) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(relsim_trin>0) %>% filter(platform_treatment==0) %>% pull(alpha), alternative = "greater") #1.1; p=.27

```



## Anonymity

```{r}
anon_pca_1d <- psych::principal(d_final %>% select(starts_with("acct")), nfactors = 1)
d_final$anon_pca_1d_scores <- anon_pca_1d$scores

anon_pca_2d <- psych::principal(d_final %>% select(starts_with("acct")), nfactors = 2)
anon_pca_2d
d_final$anon_pca_2d_scores_d1 <- anon_pca_2d$scores[,1]
d_final$anon_pca_2d_scores_d2 <- anon_pca_2d$scores[,2]

#plot()
```

### Outspokenness

```{r}
#PCA 1d

estimatr::lm_robust(beta ~ acct_shows_name + acct_shows_face + acct_vis_rwf + acct_vis_fam + acct_vis_work, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ acct_shows_name, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ acct_shows_face, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ acct_vis_rwf, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ acct_vis_fam, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ acct_vis_work, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()


```

```{r}
#PCA 2d (d1 is visibility, d2 is show name,face)

# adjusted
estimatr::lm_robust(beta ~ anon_pca_2d_scores_d1 + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ anon_pca_2d_scores_d2 + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

# unadjusted
estimatr::lm_robust(beta ~ anon_pca_2d_scores_d1, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(beta ~ anon_pca_2d_scores_d2, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()


```


### H1

```{r}
# 1d anon pca interaction
#DV: beta
mod_h1_int_anon_pca_1d_adj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_1d_scores + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
mod_h1_int_anon_pca_1d_adj$coefficients["platform_treatment:anon_pca_1d_scores"]
mod_h1_int_anon_pca_1d_adj$p.value["platform_treatment:anon_pca_1d_scores"] < .05

# unadjusted: 
mod_h1_int_anon_pca_1d_unadj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_1d_scores, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03
mod_h1_int_anon_pca_1d_unadj$coefficients["platform_treatment:anon_pca_1d_scores"]
mod_h1_int_anon_pca_1d_unadj$p.value["platform_treatment:anon_pca_1d_scores"] < .05

```



```{r}
# 2d anon pca interaction
#DV: beta
mod_h1_int_anon_pca_2d_scores_d1_adj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_2d_scores_d1 + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
mod_h1_int_anon_pca_2d_scores_d1_adj$coefficients["platform_treatment:anon_pca_2d_scores_d1"]
mod_h1_int_anon_pca_2d_scores_d1_adj$p.value["platform_treatment:anon_pca_2d_scores_d1"] < .05

# unadjusted: 
mod_h1_int_anon_pca_2d_scores_d1_unadj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_2d_scores_d1, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03
mod_h1_int_anon_pca_2d_scores_d1_unadj$coefficients["platform_treatment:anon_pca_2d_scores_d1"]
mod_h1_int_anon_pca_2d_scores_d1_unadj$p.value["platform_treatment:anon_pca_2d_scores_d1"] < .05


#DV: beta
mod_h1_int_anon_pca_2d_scores_d2_adj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_2d_scores_d2 + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
mod_h1_int_anon_pca_2d_scores_d2_adj$coefficients["platform_treatment:anon_pca_2d_scores_d2"]
mod_h1_int_anon_pca_2d_scores_d2_adj$p.value["platform_treatment:anon_pca_2d_scores_d2"] < .05

# unadjusted: 
mod_h1_int_anon_pca_2d_scores_d2_unadj <- estimatr::lm_robust(beta ~ platform_treatment*anon_pca_2d_scores_d2, data = d_final %>% filter(poster), se_type = "HC2") #sig pos interaction! p=.03
mod_h1_int_anon_pca_2d_scores_d2_unadj$coefficients["platform_treatment:anon_pca_2d_scores_d2"]
mod_h1_int_anon_pca_2d_scores_d2_unadj$p.value["platform_treatment:anon_pca_2d_scores_d2"] < .05

```



### Extremity

```{r}
estimatr::lm_robust(abs(alpha) ~ platform_treatment*anon_pca_1d_scores + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(abs(alpha) ~ anon_pca_1d_scores, data = d_final %>% filter(poster), se_type = "HC2") %>% coefplot::coefplot()

```


```{r}
#estimatr::lm_robust(abs(alpha) ~ anon_pca_1d_scores + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()

estimatr::lm_robust(abs(alpha) ~ acct_shows_name + acct_shows_face + acct_vis_rwf + acct_vis_fam + acct_vis_work, data = d_final %>% filter(poster) %>% filter(platform_treatment==1) , se_type = "HC2") %>% coefplot::coefplot()


# d_final$acct_shows_name
# d_final$acct_shows_face
# d_final$acct_vis_rwf
# d_final$acct_vis_fam
# d_final$acct_vis_work


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```




# Platform-Specific Analyses

## Facebook

```{r}
## H1
mod_h1_fb <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(primary_platform=="fb"), se_type = "HC2")
mod_h1_fb

mod_h1_fb$coefficients['platform_treatment']
mod_h1_fb$p.value['platform_treatment']/2 #p<0.001
mod_h1_fb$p.value['platform_treatment']/2 < 0.001
```


```{r}
## H2
mod_h2_fb <- estimatr::lm_robust(alpha ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(primary_platform=="fb"), se_type = "HC2")
mod_h2_fb

mod_h2_fb$coefficients['platform_treatment']
mod_h2_fb$p.value['platform_treatment']/2 #p=.36
```


```{r}
## H3
test_h3_fb <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(platform_treatment==0) %>% filter(primary_platform=="fb") %>% pull(alpha), alternative = "greater")
test_h3_fb

test_h3_fb$estimate
test_h3_fb$p.value #p<.00001
test_h3_fb$p.value <.000001

paste0("$p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h3_fb$p.value)]),"}$") %>% writeLines(., "../results/h3_fb_p.txt")

paste0("($F=",test_h3_fb$statistic %>% round(2),"$, $p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h3_fb$p.value)]),"}$, ") %>% writeLines(., "../results/h3_fb_fp.txt")
```


```{r}
## H4
test_h4_fb <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% filter(primary_platform=="fb") %>% pull(alpha), alternative = "greater")
test_h4_fb

test_h4_fb$estimate
test_h4_fb$p.value #p=.078

paste0("($F=",test_h4_fb$statistic %>% round(2),"$, $p \\approx ", test_h4_fb$p.value %>% round(.,2),"}$, ") %>% writeLines(., "../results/h4_fb_fp.txt")
```


## Twitter

```{r}
## H1
mod_h1_tw <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(primary_platform=="tw"), se_type = "HC2")
mod_h1_tw

mod_h1_tw$coefficients['platform_treatment']
mod_h1_tw$p.value['platform_treatment']/2 #p<.0001
mod_h1_tw$p.value['platform_treatment']/2 < .0001
```


```{r}
## H2
mod_h2_tw <- estimatr::lm_robust(alpha ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster) %>% filter(primary_platform=="tw"), se_type = "HC2")
mod_h2_tw

mod_h2_tw$coefficients['platform_treatment']
mod_h2_tw$p.value['platform_treatment']/2 #p=.35
```


```{r}
## H3
test_h3_tw <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha), d_final %>% filter(!poster) %>% filter(platform_treatment==0) %>% filter(primary_platform=="tw") %>% pull(alpha), alternative = "greater")
test_h3_tw

test_h3_tw$estimate
test_h3_tw$p.value #p<.003

paste0("$p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h3_tw$p.value)]),"}$") %>% writeLines(., "../results/h3_tw_p.txt")

paste0("and $F=",test_h3_tw$statistic %>% round(2),"$, $p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h3_tw$p.value)]),"}$,") %>% writeLines(., "../results/h3_tw_fp.txt")
```


```{r}
## H4
test_h4_tw <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% filter(primary_platform=="tw") %>% pull(alpha), alternative = "greater")
test_h4_tw

test_h4_tw$estimate
test_h4_tw$p.value #p=.998

paste0("and $F=",test_h4_tw$statistic %>% round(2),"$, $p \\approx ", test_h4_tw$p.value %>% round(.,2),"}$,") %>% writeLines(., "../results/h4_tw_fp.txt")

test_h4_tw_2sided <- var.test(d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha), d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% filter(primary_platform=="tw") %>% pull(alpha), alternative = "two.sided")
test_h4_tw_2sided

#paste0("($F=",test_h4_tw_2sided$statistic %>% round(2),"$, $p = ", test_h4_tw_2sided$p.value %>% round(.,2),"}$)") %>% writeLines(., "../results/h4_tw_2sided_fp.txt")

paste0("($F=",test_h4_tw_2sided$statistic %>% round(2),"$, $p< 1 \\times 10^{-",length(sig_thresholds[which(sig_thresholds>test_h4_tw_2sided$p.value)]),"}$).") %>% writeLines(., "../results/h4_tw_2sided_fp.txt")
```

#


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```




# Paper Plots

## Triple Plot

```{r}
# # plot colors
# # color_poster_online = rgb(.8,.2,.8,1)
# # color_poster_offline = rgb(.1,.5,.1,1)
# # color_lurker = rgb(.8,.1,.2,1)
# 
# color_poster_online = "#1a25b5"
# color_poster_offline = "#25b51a"
# color_lurker = "#b51a25"
# 
# pch = 16
# ref_pch = 21
# 
# density_lwd = 1
# 
# twod_coefplot_xlim = .5
# 
# pdf(file = "triple_plot.pdf", width = 8, height = 3.5)
# 
# par(mfrow = c(1,3), pty = "s", bty = "n")
# 
# plot(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], xlim = c(-twod_coefplot_xlim,twod_coefplot_xlim), ylim = c(-twod_coefplot_xlim,twod_coefplot_xlim), type = "n",
#      xlab = "Lexical Ideology Coefficient",
#      ylab = "Outspokenness Coefficient",
#      main = "")
# #abline(h=0,v=0, lty = 3, col = reference_gray)
# segments(x0 = c(0,0,0,0), x1 = c(0,1,0,-1), y0 = c(0,0,0,0), y1 = c(1, 0, -1, 0), lty = 3, col = "black")
# 
# 
# points(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], pch = pch, col = color_poster_online)
# segments(x0=mod_h2_pooled_ks$coefficients['platform_treatment'], y0=mod_h1_pooled_ks$conf.low['platform_treatment'], y1=mod_h1_pooled_ks$conf.high['platform_treatment'], col = color_poster_online)
# segments(y0=mod_h1_pooled_ks$coefficients['platform_treatment'], x0=mod_h2_pooled_ks$conf.low['platform_treatment'], x1=mod_h2_pooled_ks$conf.high['platform_treatment'], col = color_poster_online)
# 
# # mod_h2_pooled_ks$conf.low['platform_treatment']
# # mod_h2_pooled_ks$conf.high['platform_treatment']
# # 
# # mod_h1_pooled_ks$conf.low['platform_treatment']
# # mod_h1_pooled_ks$conf.high['platform_treatment']
# # 
# # 
# # legend("topleft", legend = c("Close Friend (Control)", "Someone You Just Met", "Most Liberal Person You Talk To", "Most Conservative Person You Talk To"), pch = c(ref_pch, pch, pch, pch), col = c(reference_gray, t1_coef_col, tlib_coef_col, tcon_coef_col), bty = "n", cex = lab_cex)
# # 
# 
# #points(0,0, pch = ref_pch, col = reference_gray, bg="white")
# 
# #points(0,0, pch = ref_pch, col = color_poster_offline, bg="white")
# points(0,0, pch = ref_pch, col = color_poster_offline, bg=color_poster_offline)
# 
# #####################
# 
# plot(density_poster, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
#      ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
#      type="n"  # This will not plot anything but set up the coordinates.
# )
# 
# polygon(density_poster$x, density_poster$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
# lines(density_poster, col=color_poster_offline, lwd=density_lwd)
# polygon(density_lurker$x, density_lurker$y, col=adjustcolor(color_lurker, alpha.f=0.5), border=NA)
# lines(density_lurker, col=color_lurker, lwd=density_lwd)
# #legend("topright", legend = c("Lurkers Offline", "Posters Offline"), col = c(color_lurker, color_poster_offline), pch = 15, bty = "n")
# 
# 
# ###################
# 
# plot(density_poster_online, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
#      ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
#      type="n"  # This will not plot anything but set up the coordinates.
# )
# 
# polygon(density_poster_offline$x, density_poster_offline$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
# lines(density_poster_offline, col=color_poster_offline, lwd=density_lwd)
# polygon(density_poster_online$x, density_poster_online$y, col=adjustcolor(color_poster_online, alpha.f=0.5), border=NA)
# lines(density_poster_online, col=color_poster_online, lwd=density_lwd)
# #legend("topright", legend = c("Posters Online", "Posters Offline"), col = c(color_poster_online, color_poster_offline), pch = 15, bty = "n")
# 
# 
# #################
# 
# par(xpd=T)
# 
# legend(0, .7, legend = c("Posters (Online)", "Posters (Offline)", "Lurkers (Offline)"), col = c(color_poster_online, color_poster_offline, color_lurker), pch = 16, bty = "n")
# 
# dev.off()
```


## Triple Plot (Separated)

```{r}
# plot colors
# color_poster_online = rgb(.8,.2,.8,1)
# color_poster_offline = rgb(.1,.5,.1,1)
# color_lurker = rgb(.8,.1,.2,1)

color_poster_online = "#1a25b5"
color_poster_offline = "#25b51a"
color_lurker = "#b51a25"

# w_3gang_sep = 5
# h_3gang_sep = 6
w_3gang_sep = 4
h_3gang_sep = 5

pch = 16
ref_pch = 21

density_lwd = 1

twod_coefplot_xlim = .5

pdf(file = "../results/triple_plot_sep_h12.pdf", width = w_3gang_sep, height = h_3gang_sep)

par(pty = "s", bty = "n")

plot(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], xlim = c(-twod_coefplot_xlim,twod_coefplot_xlim), ylim = c(-twod_coefplot_xlim,twod_coefplot_xlim), type = "n",
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient",
     main = "")
segments(x0 = c(0,0,0,0), x1 = c(0,1,0,-1), y0 = c(0,0,0,0), y1 = c(1, 0, -1, 0), lty = 3, col = "black")


points(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], pch = pch, col = color_poster_online)
segments(x0=mod_h2_pooled_ks$coefficients['platform_treatment'], y0=mod_h1_pooled_ks$conf.low['platform_treatment'], y1=mod_h1_pooled_ks$conf.high['platform_treatment'], col = color_poster_online)
segments(y0=mod_h1_pooled_ks$coefficients['platform_treatment'], x0=mod_h2_pooled_ks$conf.low['platform_treatment'], x1=mod_h2_pooled_ks$conf.high['platform_treatment'], col = color_poster_online)

points(0,0, pch = ref_pch, col = color_poster_offline, bg=color_poster_offline)

# par(xpd=T)
# legend(-.3,.68, legend = c("Posters (Online)", "Posters (Offline)"), col = c(color_poster_online, color_poster_offline), pch = 16, bty = "n")

dev.off()


pdf(file = "../results/triple_plot_sep_h12_legend.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(bty="n")
plot(1,1,type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
legend("center", legend = c("Posters (Online)", "Posters (Offline)"), col = c(color_poster_online, color_poster_offline), pch = 16, bty = "n")
dev.off()

#####################

pdf(file = "../results/triple_plot_sep_h3.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(pty = "s", bty = "n")
plot(density_poster, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster$x, density_poster$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
lines(density_poster, col=color_poster_offline, lwd=density_lwd)
polygon(density_lurker$x, density_lurker$y, col=adjustcolor(color_lurker, alpha.f=0.5), border=NA)
lines(density_lurker, col=color_lurker, lwd=density_lwd)

# par(xpd=T)
# legend(-3, .68, legend = c("Posters (Offline)", "Lurkers (Offline)"), col = c(color_poster_offline, color_lurker), pch = 16, bty = "n")

dev.off()

pdf(file = "../results/triple_plot_sep_h3_legend.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(bty="n")
plot(1,1,type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
legend("center", legend = c("Posters (Offline)", "Lurkers (Offline)"), col = c(color_poster_offline, color_lurker), pch = 16, bty = "n")
dev.off()

###################

pdf(file = "../results/triple_plot_sep_h4.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(pty = "s", bty = "n")
plot(density_poster_online, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster_offline$x, density_poster_offline$y, col=adjustcolor(color_poster_offline, alpha.f=0.5), border=NA)
lines(density_poster_offline, col=color_poster_offline, lwd=density_lwd)
polygon(density_poster_online$x, density_poster_online$y, col=adjustcolor(color_poster_online, alpha.f=0.5), border=NA)
lines(density_poster_online, col=color_poster_online, lwd=density_lwd)

# par(xpd=T)
# legend(-3,.68, legend = c("Posters (Online)", "Posters (Offline)"), col = c(color_poster_online, color_poster_offline), pch = 16, bty = "n")

dev.off()

pdf(file = "../results/triple_plot_sep_h4_legend.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(bty="n")
plot(1,1,type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
legend("center", legend = c("Posters (Online)", "Posters (Offline)"), col = c(color_poster_online, color_poster_offline), pch = 16, bty = "n")
dev.off()

#################


```


## Triple Plot (Separated, B&W Safe)

```{r}

plotMiniBellCurve <- function(x0, x1, y0, y1, col = "black", fill = "gray", bottom_border = F, lty = 1) {
  # Calculate the range for x values based on input coordinates
  x_coords <- seq(x0, x1, length.out = 100)
  
  # Standard normal distribution scaled to fit within the rectangle defined by y0 and y1
  # Adjust mean and sd to center and scale the curve within the box
  mean <- mean(c(x0, x1))
  sd <- (x1 - x0) / 6  # 99.7% data within +/- 3sd (covers most of the width)
  y_values <- dnorm(x_coords, mean = mean, sd = sd)
  
  # Normalize y values to fit within y0 and y1
  y_scaled <- (y_values - min(y_values)) / (max(y_values) - min(y_values)) * (y1 - y0) + y0
  
  # Draw the curve and fill below it
  lines(x_coords, y_scaled, col = col, lty = lty)
  polygon(c(x_coords, rev(x_coords)), c(rep(y0, length(x_coords)), rev(y_scaled)), col = fill, border = if_else(bottom_border, true = col, false = NA))
}

# Example usage in a plot:
x <- 1:10
y <- x^2
plot(x, y, type = "o", col = "blue", pch = 19, ylim = c(0, 110), ylab = "Y", xlab = "X")

# Add a miniature bell curve to the plot
plotMiniBellCurve(7, 9, 30, 50, col = "red", fill = "pink")

```


```{r}

minibell_vadj = -.072

# plot colors
#color_poster_online = "#1a25b5"
color_poster_offline = "#000000"
color_lurker = "#b51a25"

saturation = .75
value_lt = .75
value_dk = .75

hue_poster_online = 195
color_poster_online_lt <- hsv(hue_poster_online/360, s = saturation, v = value_lt)
color_poster_online_dk <- hsv(hue_poster_online/360, s = saturation, v = value_dk)

hue_lurker = 0
color_lurker_lt <- hsv(hue_lurker/360, s = saturation, v = value_lt)
color_lurker_dk <- hsv(hue_lurker/360, s = saturation, v = value_dk)

w_3gang_sep = 5
h_3gang_sep = 5

pch = 21

density_lty = 1
density_lwd = 1.5
twod_coefplot_xlim = .5
inset = c(-.15, 0)

pdf(file = "../results/triple_plot_sep_h12_bwsafe.pdf", width = w_3gang_sep, height = h_3gang_sep)

par(pty = "s", bty = "n")

plot(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], xlim = c(-twod_coefplot_xlim,twod_coefplot_xlim), ylim = c(-twod_coefplot_xlim,twod_coefplot_xlim), type = "n",
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient",
     main = "")
segments(x0 = c(0,0,0,0), x1 = c(0,1,0,-1), y0 = c(0,0,0,0), y1 = c(1, 0, -1, 0), lty = 3, col = "black")

points(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], pch = pch, col = color_poster_online_dk, bg = color_poster_online_dk)
segments(x0=mod_h2_pooled_ks$coefficients['platform_treatment'], y0=mod_h1_pooled_ks$conf.low['platform_treatment'], y1=mod_h1_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)
segments(y0=mod_h1_pooled_ks$coefficients['platform_treatment'], x0=mod_h2_pooled_ks$conf.low['platform_treatment'], x1=mod_h2_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)

points(0,0, pch = 16, cex = 1.5, col = "white")
points(0,0, pch = 21, col = color_poster_offline, bg="white")

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = c(color_poster_offline, color_poster_online_dk), pt.bg = c("white", color_poster_online_dk), pch = 21, bty = "n", inset = inset)

dev.off()

#####################

pdf(file = "../results/triple_plot_sep_h3_bwsafe.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(pty = "s", bty = "n")
plot(density_poster, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"
)

polygon(density_lurker$x, density_lurker$y, col=color_lurker_lt, border=NA)
lines(density_poster, col=color_poster_offline, lwd=density_lwd, lty = density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Lurkers (Offline)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_lurker_lt, fill = color_lurker_lt, bottom_border = T)

dev.off()

###################

pdf(file = "../results/triple_plot_sep_h4_bwsafe.pdf", width = w_3gang_sep, height = h_3gang_sep)
par(pty = "s", bty = "n")
plot(density_poster_online, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster_online$x, density_poster_online$y, col=color_poster_online_lt, border=NA)
lines(density_poster_offline, col=color_poster_offline, lwd=density_lwd, lty=density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_poster_online_lt, fill = color_poster_online_lt, bottom_border = T)

dev.off()


```



## Triple Plot (Separated, Non-Square)

```{r fig.width=8, fig.height=8}

h_3gang_sep_alt = h_3gang_sep*.8

minibell_vadj = -.072

# plot colors
#color_poster_online = "#1a25b5"
color_poster_offline = "#000000"
color_lurker = "#b51a25"

saturation = .75
value_lt = .75
value_dk = .75

hue_poster_online = 195
color_poster_online_lt <- hsv(hue_poster_online/360, s = saturation, v = value_lt)
color_poster_online_dk <- hsv(hue_poster_online/360, s = saturation, v = value_dk)

hue_lurker = 0
color_lurker_lt <- hsv(hue_lurker/360, s = saturation, v = value_lt)
color_lurker_dk <- hsv(hue_lurker/360, s = saturation, v = value_dk)

w_3gang_sep = 5
h_3gang_sep = 5

pch = 21

density_lty = 1
density_lwd = 1.5
twod_coefplot_xlim = .5
inset = c(-.15, 0)

pdf(file = "../results/triple_plot_sep_h12_polcomm_square.pdf", width = w_3gang_sep, height = h_3gang_sep)

par(pty = "s", bty = "n")

plot(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], xlim = c(-twod_coefplot_xlim,twod_coefplot_xlim), ylim = c(-twod_coefplot_xlim,twod_coefplot_xlim), type = "n",
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient",
     main = "")
segments(x0 = c(0,0,0,0), x1 = c(0,1,0,-1), y0 = c(0,0,0,0), y1 = c(1, 0, -1, 0), lty = 3, col = "black")

points(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], pch = pch, col = color_poster_online_dk, bg = color_poster_online_dk)
segments(x0=mod_h2_pooled_ks$coefficients['platform_treatment'], y0=mod_h1_pooled_ks$conf.low['platform_treatment'], y1=mod_h1_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)
segments(y0=mod_h1_pooled_ks$coefficients['platform_treatment'], x0=mod_h2_pooled_ks$conf.low['platform_treatment'], x1=mod_h2_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)

points(0,0, pch = 16, cex = 1.5, col = "white")
points(0,0, pch = 21, col = color_poster_offline, bg="white")

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = c(color_poster_offline, color_poster_online_dk), pt.bg = c("white", color_poster_online_dk), pch = 21, bty = "n", inset = inset)

dev.off()

#####################

pdf(file = "../results/triple_plot_sep_h3_polcomm_nonsquare.pdf", width = w_3gang_sep, height = h_3gang_sep_alt)
#par(pty = "s", bty = "n")
par(bty = "n")
plot(density_poster, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"
)

polygon(density_lurker$x, density_lurker$y, col=color_lurker_lt, border=NA)
lines(density_poster, col=color_poster_offline, lwd=density_lwd, lty = density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Lurkers (Offline)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_lurker_lt, fill = color_lurker_lt, bottom_border = T)

dev.off()

###################

pdf(file = "../results/triple_plot_sep_h4_polcomm_nonsquare.pdf", width = w_3gang_sep, height = h_3gang_sep_alt)
#par(pty = "s", bty = "n")
par(bty = "n")
plot(density_poster_online, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster_online$x, density_poster_online$y, col=color_poster_online_lt, border=NA)
lines(density_poster_offline, col=color_poster_offline, lwd=density_lwd, lty=density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_poster_online_lt, fill = color_poster_online_lt, bottom_border = T)

dev.off()


```




## Triple Plot (Separated, Improved Design + Annotation)

```{r}

h_3gang_sep_alt = h_3gang_sep*.7

minibell_vadj = -.072

# plot colors
#color_poster_online = "#1a25b5"
color_poster_offline = "#000000"
color_lurker = "#b51a25"

saturation = .75
value_lt = .75
value_dk = .75

hue_poster_online = 195
color_poster_online_lt <- hsv(hue_poster_online/360, s = saturation, v = value_lt)
color_poster_online_dk <- hsv(hue_poster_online/360, s = saturation, v = value_dk)

hue_lurker = 0
color_lurker_lt <- hsv(hue_lurker/360, s = saturation, v = value_lt)
color_lurker_dk <- hsv(hue_lurker/360, s = saturation, v = value_dk)

w_3gang_sep = 5
h_3gang_sep = 5

pch = 21

density_lty = 1
density_lwd = 1.5
twod_coefplot_xlim = .5
inset = c(-.15, 0)

pdf(file = "../results/triple_plot_sep_h12_polcomm_square.pdf", width = w_3gang_sep, height = h_3gang_sep)

par(pty = "s", bty = "n")

plot(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], xlim = c(-twod_coefplot_xlim,twod_coefplot_xlim), ylim = c(-twod_coefplot_xlim,twod_coefplot_xlim), type = "n",
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient",
     main = "")
segments(x0 = c(0,0,0,0), x1 = c(0,1,0,-1), y0 = c(0,0,0,0), y1 = c(1, 0, -1, 0), lty = 3, col = "black")

points(mod_h2_pooled_ks$coefficients['platform_treatment'], mod_h1_pooled_ks$coefficients['platform_treatment'], pch = pch, col = color_poster_online_dk, bg = color_poster_online_dk)
segments(x0=mod_h2_pooled_ks$coefficients['platform_treatment'], y0=mod_h1_pooled_ks$conf.low['platform_treatment'], y1=mod_h1_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)
segments(y0=mod_h1_pooled_ks$coefficients['platform_treatment'], x0=mod_h2_pooled_ks$conf.low['platform_treatment'], x1=mod_h2_pooled_ks$conf.high['platform_treatment'], col = color_poster_online_dk)

points(0,0, pch = 16, cex = 1.5, col = "white")
points(0,0, pch = 21, col = color_poster_offline, bg="white")

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = c(color_poster_offline, color_poster_online_dk), pt.bg = c("white", color_poster_online_dk), pch = 21, bty = "n", inset = inset)

dev.off()

#####################

pdf(file = "../results/triple_plot_sep_h3_polcomm_nonsquare.pdf", width = w_3gang_sep, height = h_3gang_sep_alt)
#par(pty = "s", bty = "n")
par(bty = "n")
plot(density_poster, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster$y, density_lurker$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"
)

polygon(density_lurker$x, density_lurker$y, col=color_lurker_lt, border=NA)
lines(density_poster, col=color_poster_offline, lwd=density_lwd, lty = density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Lurkers (Offline)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_lurker_lt, fill = color_lurker_lt, bottom_border = T)

dev.off()

###################

pdf(file = "../results/triple_plot_sep_h4_polcomm_nonsquare.pdf", width = w_3gang_sep, height = h_3gang_sep_alt)
#par(pty = "s", bty = "n")
par(bty = "n")
plot(density_poster_online, main="", xlab="Lexical Ideology", ylab="Density", xlim = c(-4,4),
     #ylim=range(c(density_poster_online$y, density_poster_offline$y)),  # adjust y-axis limits
     ylim=c(0,.6),
     type="n"  # This will not plot anything but set up the coordinates.
)

polygon(density_poster_online$x, density_poster_online$y, col=color_poster_online_lt, border=NA)
lines(density_poster_offline, col=color_poster_offline, lwd=density_lwd, lty=density_lty)

par(xpd=T)
legend("topright", legend = c("Posters (Offline)", "Posters (Online)"), col = "white", pch = 16, bty = "n", inset = inset)

plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj, col = color_poster_offline, fill = NA, lty = density_lty)
plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj, col = color_poster_online_lt, fill = color_poster_online_lt, bottom_border = T)

dev.off()


```

# Tufte Plots

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 3)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```



```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)

pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h3, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Lurkers (Offline)"),
             cols   = c(color_poster_offline, color_lurker_dk),
             fills  = c(NA, color_lurker_lt))

# plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj,
#                   col = color_poster_offline, fill = NA)
# plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj,
#                   col = color_lurker_dk, fill = color_lurker_lt,
#                   bottom_border = TRUE)
dev.off()
```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)

pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster_online, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h4, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c(NA, color_poster_online_lt))

# plotMiniBellCurve(1, 2, .644+minibell_vadj, .669+minibell_vadj,
#                   col = color_poster_offline, fill = NA)
# plotMiniBellCurve(1, 2, .603+minibell_vadj, .628+minibell_vadj,
#                   col = color_poster_online_dk, fill = color_poster_online_lt,
#                   bottom_border = TRUE)
dev.off()


```




# Even better Plots

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 3)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
## Overlay per-bin ratio of two distributions (A/B) over an existing plot
## x_num: numeric vector for A (numerator); x_den: numeric vector for B (denominator)
## breaks: histogram breaks used for both (choose to match your xlim)
add_ratio_hist <- function(x_num, x_den,
                           breaks = seq(-4, 4, by = 0.5),
                           ylim_ratio = c(0, 2),
                           stem_lwd = 6,
                           stem_col = "black",
                           fill_alpha = 0.10,
                           axis_label = "Bin share ratio (A/B)") {
  h_num <- hist(x_num, breaks = breaks, plot = FALSE)
  h_den <- hist(x_den, breaks = breaks, plot = FALSE)

  ## normalize to *shares* so sample size differences don't drive the ratio
  p_num <- h_num$counts / sum(h_num$counts)
  p_den <- h_den$counts / sum(h_den$counts)

  eps <- 1e-12
  ratio <- p_num / pmax(p_den, eps)
  mids  <- h_num$mids
  bw    <- diff(breaks)[1]

  ## Overlay on a new right-axis coordinate system
  par(new = TRUE)
  plot(NA, NA,
       xlim = range(breaks), ylim = ylim_ratio,
       xlab = "", ylab = "", axes = FALSE, type = "n")

  ## Optional faint fill bars (very light so densities remain legible)
  rect(mids - bw/2, 0, mids + bw/2, pmin(ratio, ylim_ratio[2]),
       border = NA, col = adjustcolor("black", alpha.f = fill_alpha))

  ## Black stems to make the ratio visible in print
  segments(mids, 0, mids, pmin(ratio, ylim_ratio[2]),
           col = stem_col, lwd = stem_lwd)

  ## Right axis + label
  axis(4)
  mtext(axis_label, side = 4, line = 2)
}




```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```

```{r}
hist_rat_bw = 1
hist_rat_xmag = 4.5
hist_rat_xlim = c(-hist_rat_xmag, hist_rat_xmag)

```


```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)

pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h3, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline)

## choose breaks that match your xlim and data grain
h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

add_ratio_hist(
  x_num = d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha),
  x_den = d_final %>% filter(!poster) %>% filter(platform_treatment==0) %>% pull(alpha),
  breaks = h3_breaks,
  ylim_ratio = c(0, 2),           # adjust if your ratios exceed 2
  stem_lwd = 6,                    # keeps bold but not overpowering
  stem_col = "black",
  fill_alpha = 0.08,               # very light so curves read clearly
  axis_label = "Share ratio (Posters/Lurkers)"
)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Lurkers (Offline)"),
             cols   = c(color_poster_offline, color_lurker_dk),
             fills  = c(NA, color_lurker_lt))

dev.off()
```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)

pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster_online, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h4, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline)

h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

add_ratio_hist(
  x_num =  d_final %>% filter(poster) %>% filter(platform_treatment==1) %>% pull(alpha),
  x_den =  d_final %>% filter(poster) %>% filter(platform_treatment==0) %>% pull(alpha),
  breaks = h4_breaks,
  ylim_ratio = c(0, 1.6),          # "flat" near 1 reads well here
  stem_lwd = 6,
  stem_col = "black",
  fill_alpha = 0.08,
  axis_label = "Share ratio (Online/Offline)"
)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c(NA, color_poster_online_lt))

dev.off()


```



# Even better plots 2

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 3)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
## Overlay per-bin ratio of two distributions (A/B) over an existing plot
## x_num: numeric vector for A (numerator); x_den: numeric vector for B (denominator)
## breaks: histogram breaks used for both (choose to match your xlim)
## Overlay per-bin ratio of two distributions (A/B) over an existing plot
## - No shaded fill
## - Each bin drawn as a vertical stem at the integer mid AND a horizontal cap
##   spanning exactly 1 unit (mid - 0.5 to mid + 0.5), aligned to integer centers.
add_ratio_hist <- function(x_num, x_den,
                           breaks = seq(-4.5, 4.5, by = 1),  # edges at .5 -> mids at integers
                           ylim_ratio = c(0, 2),
                           stem_lwd = 6,
                           stem_col = "black",
                           cap_lwd  = 2,                      # thinner horizontal caps
                           axis_label = "Bin share ratio (A/B)") {
  ## ensure mids are integers by forcing .5-spaced edges
  if (abs(diff(breaks)[1] - 1) > .Machine$double.eps^0.5 ||
      any(abs(breaks - round(breaks) - 0.5) > 1e-8)) {
    rng <- range(c(x_num, x_den), finite = TRUE)
    bmin <- floor(rng[1]) - 0.5
    bmax <- ceiling(rng[2]) + 0.5
    breaks <- seq(bmin, bmax, by = 1)
  }

  h_num <- hist(x_num, breaks = breaks, plot = FALSE)
  h_den <- hist(x_den, breaks = breaks, plot = FALSE)

  ## normalize to shares before ratio
  p_num <- h_num$counts / sum(h_num$counts)
  p_den <- h_den$counts / sum(h_den$counts)

  eps   <- 1e-12
  ratio <- p_num / pmax(p_den, eps)
  mids  <- h_num$mids    # will be integers by construction
  bw    <- diff(breaks)[1]  # = 1

  ## Overlay on right axis
  par(new = TRUE)
  plot(NA, NA,
       xlim = range(breaks), ylim = ylim_ratio,
       xlab = "", ylab = "", axes = FALSE, type = "n")

  ## Draw vertical stems (at integer mids)
  yvals <- pmin(ratio, ylim_ratio[2])
  segments(mids, 0, mids, yvals, col = stem_col, lwd = stem_lwd)

  ## Draw horizontal caps spanning exactly one unit (bin width = 1)
  segments(mids - bw/2, yvals, mids + bw/2, yvals, col = stem_col, lwd = cap_lwd)

  ## Right axis
  axis(4)
  mtext(axis_label, side = 4, line = 2)
}



```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```

```{r}
# hist_rat_bw = 1
# hist_rat_xmag = 4.5
# hist_rat_xlim = c(-hist_rat_xmag, hist_rat_xmag)

hist_rat_bw   <- 1
hist_rat_xmag <- 4.5
h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)  # -4.5..4.5
h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)


```


```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)

pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h3, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline)

## choose breaks that match your xlim and data grain
#h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment == 0) %>% pull(alpha),
  x_den = d_final %>% filter(!poster, platform_treatment == 0) %>% pull(alpha),
  breaks = h3_breaks,
  ylim_ratio = c(0, 2),
  stem_lwd = 6,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Share ratio (Posters/Lurkers)"
)


quiet_legend("topright",
             labels = c("Posters (Offline)", "Lurkers (Offline)"),
             cols   = c(color_poster_offline, color_lurker_dk),
             fills  = c(NA, color_lurker_lt))

dev.off()
```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)

pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster_online, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h4, type = "n")

abline(v = 0, col = ref_col, lty = 3)

polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline)

#h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment == 1) %>% pull(alpha),
  x_den = d_final %>% filter(poster, platform_treatment == 0) %>% pull(alpha),
  breaks = h4_breaks,
  ylim_ratio = c(0, 1.6),
  stem_lwd = 6,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Share ratio (Online/Offline)"
)


quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c(NA, color_poster_online_lt))

dev.off()


```






# Even better plots 3

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 3)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
## Ratio overlay aligned to current plot:
## - no shaded area
## - unit-wide caps centered on integers
## - x-scale taken from par('usr') of the existing plot
add_ratio_hist <- function(x_num, x_den,
                           breaks = NULL,            # if NULL, we derive integer-centered breaks from data & current xlim
                           ylim_ratio = c(0, 2),
                           stem_lwd = 6,
                           stem_col = "black",
                           cap_lwd  = 2,
                           axis_label = "Bin share ratio (A/B)") {

  ## Get current plot x-limits (so we align scales)
  usr <- par("usr")          # c(xmin, xmax, ymin, ymax)
  xlim_now <- usr[1:2]

  ## Build integer-centered breaks (edges at n  0.5) spanning current xlim
  if (is.null(breaks)) {
    left  <- floor(xlim_now[1]) - 0.5
    right <- ceiling(xlim_now[2]) + 0.5
    breaks <- seq(left, right, by = 1)
  } else {
    ## Force them to be unit-width & .5-offset; if not, coerce to match xlim
    if (abs(diff(breaks)[1] - 1) > .Machine$double.eps^0.5 ||
        any(abs(breaks - round(breaks) - 0.5) > 1e-8)) {
      left  <- floor(xlim_now[1]) - 0.5
      right <- ceiling(xlim_now[2]) + 0.5
      breaks <- seq(left, right, by = 1)
    }
  }

  h_num <- hist(x_num, breaks = breaks, plot = FALSE)
  h_den <- hist(x_den, breaks = breaks, plot = FALSE)

  ## Normalize to shares before ratio
  p_num <- h_num$counts / sum(h_num$counts)
  p_den <- h_den$counts / sum(h_den$counts)

  eps   <- 1e-12
  ratio <- p_num / pmax(p_den, eps)
  mids  <- h_num$mids   # integers by construction
  bw    <- 1

  ## Overlay on the SAME x-scale
  par(new = TRUE)
  plot(NA, NA,
       xlim = xlim_now, ylim = ylim_ratio,
       xlab = "", ylab = "", axes = FALSE, type = "n",
       xaxs = "i", yaxs = "i")

  yvals <- pmin(ratio, ylim_ratio[2])

  ## Vertical stems at integer centers
  segments(mids, 0, mids, yvals, col = stem_col, lwd = stem_lwd, lend = 1)

  ## Horizontal caps spanning exactly one unit
  segments(mids - bw/2, yvals, mids + bw/2, yvals, col = stem_col, lwd = cap_lwd, lend = 1)

  ## Right axis
  axis(4)
  mtext(axis_label, side = 4, line = 2)
}


```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```

```{r}
# hist_rat_bw = 1
# hist_rat_xmag = 4.5
# hist_rat_xlim = c(-hist_rat_xmag, hist_rat_xmag)

hist_rat_bw   <- 1
hist_rat_xmag <- 4.5
h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)  # -4.5..4.5
h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)


```


```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)

pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

## exact x-scale, well add our own integer ticks
plot(density_poster, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h3, type = "n", xaxs = "i", xaxt = "n")

## integer ticks aligned with histogram mids
axis(1, at = seq(-4, 4, by = 1), labels = seq(-4, 4, by = 1))

abline(v = 0, col = ref_col, lty = 3)
polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline)

## Breaks centered on integers across current xlim
h3_breaks <- seq(-4.5, 4.5, by = 1)

add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  x_den = d_final %>% filter(!poster, platform_treatment==0) %>% pull(alpha),
  breaks = h3_breaks,
  ylim_ratio = c(0, 2),
  stem_lwd = 6,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Share ratio (Posters/Lurkers)"
)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Lurkers (Offline)"),
             cols   = c(color_poster_offline, color_lurker_dk),
             fills  = c(NA, color_lurker_lt))

dev.off()

```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)

pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)
par_defaults()

plot(density_poster_online, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-4, 4), ylim = ylim_h4, type = "n", xaxs = "i", xaxt = "n")

axis(1, at = seq(-4, 4, by = 1), labels = seq(-4, 4, by = 1))

abline(v = 0, col = ref_col, lty = 3)
polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline)

h4_breaks <- seq(-4.5, 4.5, by = 1)

add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==1) %>% pull(alpha),
  x_den = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  breaks = h4_breaks,
  ylim_ratio = c(0, 1.6),
  stem_lwd = 6,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Share ratio (Online/Offline)"
)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c(NA, color_poster_online_lt))

dev.off()


```



# Even better plots 4

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 2)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
## Ratio overlay aligned to current plot:
## - no shaded area
## - unit-wide caps centered on integers
## - x-scale taken from par('usr') of the existing plot
add_ratio_hist <- function(x_num, x_den,
                           breaks = NULL,            # if NULL, we derive integer-centered breaks from data & current xlim
                           ylim_ratio = c(0, 2),
                           stem_lwd = 6,
                           stem_col = "black",
                           cap_lwd  = 2,
                           axis_label = "Bin share ratio (A/B)") {

  ## Get current plot x-limits (so we align scales)
  usr <- par("usr")          # c(xmin, xmax, ymin, ymax)
  xlim_now <- usr[1:2]

  ## Build integer-centered breaks (edges at n  0.5) spanning current xlim
  if (is.null(breaks)) {
    left  <- floor(xlim_now[1]) - 0.5
    right <- ceiling(xlim_now[2]) + 0.5
    breaks <- seq(left, right, by = 1)
  } else {
    ## Force them to be unit-width & .5-offset; if not, coerce to match xlim
    if (abs(diff(breaks)[1] - 1) > .Machine$double.eps^0.5 ||
        any(abs(breaks - round(breaks) - 0.5) > 1e-8)) {
      left  <- floor(xlim_now[1]) - 0.5
      right <- ceiling(xlim_now[2]) + 0.5
      breaks <- seq(left, right, by = 1)
    }
  }

  h_num <- hist(x_num, breaks = breaks, plot = FALSE)
  h_den <- hist(x_den, breaks = breaks, plot = FALSE)

  ## Normalize to shares before ratio
  p_num <- h_num$counts / sum(h_num$counts)
  p_den <- h_den$counts / sum(h_den$counts)

  eps   <- 1e-12
  ratio <- p_num / pmax(p_den, eps)
  mids  <- h_num$mids   # integers by construction
  bw    <- 1

  ## Overlay on the SAME x-scale
  par(new = TRUE)
  plot(NA, NA,
       xlim = xlim_now, ylim = ylim_ratio,
       xlab = "", ylab = "", axes = FALSE, type = "n",
       xaxs = "i", yaxs = "i")

  yvals <- pmin(ratio, ylim_ratio[2])

  ## Vertical stems at integer centers
  segments(mids, 0, mids, yvals, col = stem_col, lwd = stem_lwd, lend = 1)

  ## Horizontal caps spanning exactly one unit
  segments(mids - bw/2, yvals, mids + bw/2, yvals, col = stem_col, lwd = cap_lwd, lend = 1)

  ## Right axis
  axis(4)
  mtext(axis_label, side = 4, line = 3, las = 3)
}


```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Coefficient",
     ylab = "Outspokenness Coefficient")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```

```{r}
hist_rat_bw   <- 1
hist_rat_xmag <- 4.5
h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)  # -4.5..4.5
h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

dist_xmag = 4
dist_xaxt_mag = 3

black_lwd = 1.75
stem_lwd = 3
```


```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)
pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)

## Simple, plot-specific par: extra top & right margin
par(bty = "n", las = 1, mar = c(4, 4, 3.5, 4))  # bottom, left, top, right

plot(density_poster, main = "", xlab = "Lexical Ideology (Standard Deviations)", ylab = "Density",
     xlim = c(-dist_xmag, dist_xmag), ylim = ylim_h3, type = "n", xaxs = "i", xaxt = "n")
axis(1, at = seq(-dist_xaxt_mag, dist_xaxt_mag, by = 1))
abline(v = 0, col = ref_col, lty = 3)

polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline, lwd = black_lwd)

h3_breaks <- seq(-4.5, 4.5, by = 1)
add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  x_den = d_final %>% filter(!poster, platform_treatment==0) %>% pull(alpha),
  breaks = h3_breaks,
  ylim_ratio = c(0, 2),
  stem_lwd = stem_lwd,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Density Ratio (Posters/Lurkers)"
)

abline(h = 0, col = "gray90", lwd = 1.5)

## Legend in the title space
par(xpd = NA)
legend("top", inset = -0.25,
       horiz = TRUE,
       legend = c("Posters (Offline)", "Lurkers (Offline)"),
       col = c(color_poster_offline, color_lurker_dk),
       pt.bg = c(NA, color_lurker_lt), pch = 21, bty = "n", cex = 0.9)

dev.off()


```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)
pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)

## Same margins: room above + room for right axis label
par(bty = "n", las = 1, mar = c(4, 4, 3.5, 4))

plot(density_poster_online, main = "", xlab = "Lexical Ideology", ylab = "Density",
     xlim = c(-dist_xmag, dist_xmag), ylim = ylim_h4, type = "n", xaxs = "i", xaxt = "n")
axis(1, at = seq(-dist_xaxt_mag, dist_xaxt_mag, by = 1))
abline(v = 0, col = ref_col, lty = 3)

polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline, lwd = black_lwd)

h4_breaks <- seq(-4.5, 4.5, by = 1)
add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==1) %>% pull(alpha),
  x_den = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  breaks = h4_breaks,
  ylim_ratio = c(0, 1.6),
  stem_lwd = stem_lwd,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Density Ratio (Online/Offline)"
)

par(xpd = NA)
legend("top", inset = -0.25, horiz = TRUE,
       legend = c("Posters (Offline)", "Posters (Online)"),
       col = c(color_poster_offline, color_poster_online_dk),
       pt.bg = c(NA, color_poster_online_lt), pch = 21, bty = "n", cex = 0.9)

dev.off()


```


# Even better plots 5

```{r}
## OkabeIto palette (colorblind safe)
oi <- list(
  black          = "#000000",
  blue           = "#0072B2",
  sky            = "#56B4E9",
  vermilion      = "#D55E00"
)

## Assign roles
color_poster_offline   <- oi$black
color_poster_online_dk <- oi$blue
color_poster_online_lt <- adjustcolor(oi$sky, alpha.f = 0.40)
color_lurker_dk        <- oi$vermilion
color_lurker_lt        <- adjustcolor(oi$vermilion, alpha.f = 0.30)

## Reference lines in black
ref_col <- "black"

## Reset to base R defaults for spacing/weights
par_defaults <- function(square = FALSE) {
  par(
    bty = "n",
    las = 1,
    pty = if (square) "s" else "m"
  )
}

draw_origin <- function() {
  abline(h = 0, v = 0, col = ref_col, lty = 2)
}

draw_ci <- function(x, y, xlo, xhi, ylo, yhi, col) {
  arrows(x0 = xlo, y0 = y, x1 = xhi, y1 = y,
         angle = 90, code = 3, length = 0.04, col = col)
  arrows(x0 = x, y0 = ylo, x1 = x, y1 = yhi,
         angle = 90, code = 3, length = 0.04, col = col)
}

quiet_legend <- function(x, labels, cols, fills, pch = 21, inset = c(-.12, 0)) {
  par(xpd = NA)
  legend(
    x, legend = labels,
    pt.bg = fills, col = cols, pch = pch, bty = "n",
    inset = inset, pt.cex = 1, cex = 0.9
  )
}

```


```{r}
## Ratio overlay aligned to current plot:
## - no shaded area
## - unit-wide caps centered on integers
## - x-scale taken from par('usr') of the existing plot
add_ratio_hist <- function(x_num, x_den,
                           breaks = NULL,            # if NULL, we derive integer-centered breaks from data & current xlim
                           ylim_ratio = c(0, 2),
                           stem_lwd = 6,
                           stem_col = "black",
                           cap_lwd  = 2,
                           axis_label = "Bin share ratio (A/B)") {

  ## Get current plot x-limits (so we align scales)
  usr <- par("usr")          # c(xmin, xmax, ymin, ymax)
  xlim_now <- usr[1:2]

  ## Build integer-centered breaks (edges at n  0.5) spanning current xlim
  if (is.null(breaks)) {
    left  <- floor(xlim_now[1]) - 0.5
    right <- ceiling(xlim_now[2]) + 0.5
    breaks <- seq(left, right, by = 1)
  } else {
    ## Force them to be unit-width & .5-offset; if not, coerce to match xlim
    if (abs(diff(breaks)[1] - 1) > .Machine$double.eps^0.5 ||
        any(abs(breaks - round(breaks) - 0.5) > 1e-8)) {
      left  <- floor(xlim_now[1]) - 0.5
      right <- ceiling(xlim_now[2]) + 0.5
      breaks <- seq(left, right, by = 1)
    }
  }

  h_num <- hist(x_num, breaks = breaks, plot = FALSE)
  h_den <- hist(x_den, breaks = breaks, plot = FALSE)

  ## Normalize to shares before ratio
  p_num <- h_num$counts / sum(h_num$counts)
  p_den <- h_den$counts / sum(h_den$counts)

  eps   <- 1e-12
  ratio <- p_num / pmax(p_den, eps)
  mids  <- h_num$mids   # integers by construction
  bw    <- 1

  ## Overlay on the SAME x-scale
  par(new = TRUE)
  plot(NA, NA,
       xlim = xlim_now, ylim = ylim_ratio,
       xlab = "", ylab = "", axes = FALSE, type = "n",
       xaxs = "i", yaxs = "i")

  yvals <- pmin(ratio, ylim_ratio[2])

  ## Vertical stems at integer centers
  segments(mids, 0, mids, yvals, col = stem_col, lwd = stem_lwd, lend = 1)

  ## Horizontal caps spanning exactly one unit
  segments(mids - bw/2, yvals, mids + bw/2, yvals, col = stem_col, lwd = cap_lwd, lend = 1)

  ## Right axis
  axis(4)
  mtext(axis_label, side = 4, line = 3, las = 3)
}


```


```{r}
twod_coefplot_xlim <- 0.5
pdf("../results/triple_plot_sep_h12_polcomm_square.pdf",
    width = w_3gang_sep, height = h_3gang_sep)

par_defaults(square = TRUE)

plot(NA, NA,
     xlim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     ylim = c(-twod_coefplot_xlim, twod_coefplot_xlim),
     xlab = "Lexical Ideology Effect\n   <-  Leftward Falsification  |  Rightward Falsification. ->",
     ylab = "Outspokenness Effect\n<-  Less Outspoken  |  More Outspoken ->")

draw_origin()

x   <- unname(mod_h2_pooled_ks$coefficients["platform_treatment"])
y   <- unname(mod_h1_pooled_ks$coefficients["platform_treatment"])
xlo <- unname(mod_h2_pooled_ks$conf.low["platform_treatment"])
xhi <- unname(mod_h2_pooled_ks$conf.high["platform_treatment"])
ylo <- unname(mod_h1_pooled_ks$conf.low["platform_treatment"])
yhi <- unname(mod_h1_pooled_ks$conf.high["platform_treatment"])

draw_ci(x, y, xlo, xhi, ylo, yhi, col = color_poster_online_dk)

points(0, 0, pch = 21, col = color_poster_offline, bg = "white", cex = 1.2)
points(x, y, pch = 21, col = color_poster_online_dk,
       bg = color_poster_online_dk, cex = 1.2)

quiet_legend("topright",
             labels = c("Posters (Offline)", "Posters (Online)"),
             cols   = c(color_poster_offline, color_poster_online_dk),
             fills  = c("white", color_poster_online_dk))
dev.off()

```

```{r}
hist_rat_bw   <- 1
hist_rat_xmag <- 4.5
h3_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)  # -4.5..4.5
h4_breaks <- seq(-hist_rat_xmag, hist_rat_xmag, by = hist_rat_bw)

dist_xmag = 3.75
dist_xaxt_mag = 3

black_lwd = 1.75
stem_lwd = 3
```


```{r}
ylim_h3 <- c(0, max(c(density_poster$y, density_lurker$y))*1.05)
pdf("../results/triple_plot_sep_h3_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)

## Simple, plot-specific par: extra top & right margin
par(bty = "n", las = 1, mar = c(4, 4, 3.5, 4))  # bottom, left, top, right

## H3 figure
plot(density_poster,
     main = "",
     xlab = "Lexical Ideology (Standard Deviations)",
     ylab = "Density",
     xlim = c(-dist_xmag, dist_xmag),
     ylim = ylim_h3,
     type = "n",
     xaxs = "i",
     yaxs = "i",          # <-- add this
     xaxt = "n")

axis(1, at = seq(-dist_xaxt_mag, dist_xaxt_mag, by = 1))

polygon(density_lurker$x, density_lurker$y, col = color_lurker_lt, border = NA)
lines(density_poster, col = color_poster_offline, lwd = black_lwd)

h3_breaks <- seq(-4.5, 4.5, by = 1)
add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  x_den = d_final %>% filter(!poster, platform_treatment==0) %>% pull(alpha),
  breaks = h3_breaks,
  ylim_ratio = c(0, 2),
  stem_lwd = stem_lwd,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Density Ratio (Posters/Lurkers)"
)

## Legend in the title space
par(xpd = NA)
segments(x0 = -dist_xmag, x1 = dist_xmag, y0 = 0, col = ref_col, lty = 1)
# legend("top", inset = -0.25,
#        horiz = TRUE,
#        legend = c("Posters (Offline)", "Lurkers (Offline)"),
#        col = c(color_poster_offline, color_lurker_dk),
#        pt.bg = c(NA, color_lurker_lt), pch = 21, bty = "n", cex = 0.9)

par(xpd = NA)                       # allow drawing in the margin
usr <- par("usr")
xmid <- mean(usr[1:2])
ytop <- usr[4] + 0.07*diff(usr[3:4])  # ~7% plot height above the top; tweak as needed
legend(x = xmid+1, y = ytop, xjust = 0.5, yjust = 0,   # center over the plot
       horiz = TRUE,
       legend = c("Posters (Offline)", "Lurkers (Offline)", "Ratio"),
       col    = c(color_poster_offline,  color_lurker_dk, "black"),
       pt.bg  = c(NA,                    color_lurker_lt, NA),
       pch    = c(21, 21, 124),
       pt.cex = c(1,  1,  1.4),
       lty    = c(0,  0,  0),
       lwd    = c(NA, NA, NA),
       bty    = "n", cex = 0.9,
       x.intersp = 0.25,
       text.width = max(strwidth(c("Posters (Offline)",
                                   "Lurkers (Offline)",
                                   "Ratio"))) * 1.1)

dev.off()


```


```{r}
ylim_h4 <- c(0, max(c(density_poster_online$y, density_poster_offline$y))*1.05)
pdf("../results/triple_plot_sep_h4_polcomm_nonsquare.pdf",
    width = w_3gang_sep, height = h_3gang_sep_alt)

## Same margins: room above + room for right axis label
par(bty = "n", las = 1, mar = c(4, 4, 3.5, 4))

## H4 figure
plot(density_poster_online,
     main = "",
     xlab = "Lexical Ideology (Standard Deviations)",
     ylab = "Density",
     xlim = c(-dist_xmag, dist_xmag),
     ylim = ylim_h4,
     type = "n",
     xaxs = "i",
     yaxs = "i",          # <-- add this
     xaxt = "n")

axis(1, at = seq(-dist_xaxt_mag, dist_xaxt_mag, by = 1))

polygon(density_poster_online$x, density_poster_online$y,
        col = color_poster_online_lt, border = NA)
lines(density_poster_offline, col = color_poster_offline, lwd = black_lwd)

h4_breaks <- seq(-4.5, 4.5, by = 1)
add_ratio_hist(
  x_num = d_final %>% filter(poster, platform_treatment==1) %>% pull(alpha),
  x_den = d_final %>% filter(poster, platform_treatment==0) %>% pull(alpha),
  breaks = h4_breaks,
  ylim_ratio = c(0, 2),
  stem_lwd = stem_lwd,
  stem_col = "black",
  cap_lwd  = NA,
  axis_label = "Density Ratio (Online/Offline)"
)

par(xpd = NA)
segments(x0 = -dist_xmag, x1 = dist_xmag, y0 = 0, col = ref_col, lty = 1)
# legend("top", inset = -0.25, horiz = TRUE,
#        legend = c("Posters (Offline)", "Posters (Online)"),
#        col = c(color_poster_offline, color_poster_online_dk),
#        pt.bg = c(NA, color_poster_online_lt), pch = 21, bty = "n", cex = 0.9)

par(xpd = NA)                       # allow drawing in the margin
usr <- par("usr")
xmid <- mean(usr[1:2])
ytop <- usr[4] + 0.07*diff(usr[3:4])  # ~7% plot height above the top; tweak as needed
legend(x = xmid+1, y = ytop, xjust = 0.5, yjust = 0,   # center over the plot
       horiz = TRUE,
       legend = c("Posters (Offline)", "Posters (Online)", "Ratio"),
       col    = c(color_poster_offline,  color_poster_online_dk, "black"),
       pt.bg  = c(NA,                    color_poster_online_lt, NA),
       pch    = c(21, 21, 124),
       pt.cex = c(1,  1,  1.4),
       lty    = c(0,  0,  0),
       lwd    = c(NA, NA, NA),
       bty    = "n", cex = 0.9,
       x.intersp = 0.25,
       text.width = max(strwidth(c("Posters (Offline)",
                                   "Posters (Online)",
                                   "Ratio"))) * 1.1)







dev.off()


```



# Tables

```{r}
library(texreg)

include.ci = FALSE
single.row = T
float.pos = "h!"
tabular = F
table = F

```


## H1 and H2

```{r}
# H1 H2 pre-reg only

# mod_h1_pooled_ks <- estimatr::lm_robust(beta ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
# (mod_h1_pooled_ks$p.value['platform_treatment']/2) < .00001
# 
# mod_h2_pooled_ks <- estimatr::lm_robust(alpha ~ platform_treatment + age_dec + IDEO + PartyID7 + college + poc + male, data = d_final %>% filter(poster), se_type = "HC2")
# (mod_h2_pooled_ks$p.value['platform_treatment']/2) < .05 #p=.36

texreg(list("Outspokenness" = mod_h1_pooled_ks, "Lexical Ideology" = mod_h2_pooled_ks),
       custom.coef.names = c("Intercept", "Platform Treatment", "Age (Decades)", "5-Point Ideology", "7-Point Partisanship", "College", "POC", "Male"),
       include.ci = include.ci,
       single.row = single.row,
       float.pos = float.pos,
       tabular = tabular,
       table = table,
       file = "../results/ch3_h12_pooled.tex",
       label = "tab:ch3_h12_pooled",
       caption = "Platform Treatment Effects"
       )
```


```{r}
#
texreg(list("Pooled" = mod_h1_pooled_ks, "Facebook" = mod_h1_fb, "Twitter" = mod_h1_tw),
       custom.coef.names = c("Intercept", "Platform Treatment", "Age (Decades)", "5-Point Ideology", "7-Point Partisanship", "College", "POC", "Male"),
       include.ci = include.ci,
       single.row = single.row,
       float.pos = float.pos,
       tabular = tabular,
       table = table,
       file = "../results/ch3_h1_ptf.tex",
       label = "tab:ch3_h1_ptf",
       caption = "Platform Treatment Effects: Outspokenness (H1)"
)


texreg(list("Pooled" = mod_h2_pooled_ks, "Facebook" = mod_h2_fb, "Twitter" = mod_h2_tw),
       custom.coef.names = c("Intercept", "Platform Treatment", "Age (Decades)", "5-Point Ideology", "7-Point Partisanship", "College", "POC", "Male"),
       include.ci = include.ci,
       single.row = single.row,
       float.pos = float.pos,
       tabular = tabular,
       table = table,
       file = "../results/ch3_h2_ptf.tex",
       label = "tab:ch3_h2_ptf",
       caption = "Platform Treatment Effects: Lexical Ideology (H2)"
)

#mod_h2_pooled_ks
```



```{r}
# H1 with int relsim

texreg(list("Pooled" = mod_h1_pooled_ks, "Facebook" = mod_h1_fb, "Twitter" = mod_h1_tw, "$\\times$ Likemindedness" = mod_h1_int_relsim_adj),
       custom.coef.names = c("Intercept", "Platform Treatment", "Age (Decades)", "5-Point Ideology", "7-Point Partisanship", "College", "POC", "Male", "Likemindedness", "Platform Treatment \\\\ $\\times$ Likemindedness"),
       include.ci = include.ci,
       single.row = single.row,
       float.pos = float.pos,
       tabular = tabular,
       table = table,
       file = "../results/ch3_h1_ptfr.tex",
       label = "tab:ch3_h1_ptfr",
       caption = "Platform Treatment Effects: Outspokenness (H1)"
)

#mod_h2_pooled_ks
```


```{r}
# likemindedness subset analyses

d_final %>% filter(poster)
d_final %>% filter(poster) %>% filter(relsim_trin<0) %>% nrow
d_final %>% filter(poster) %>% filter(relsim_trin==0) %>% nrow
d_final %>% filter(poster) %>% filter(relsim_trin>0) %>% nrow

n_poster <- d_final %>% filter(poster) %>% filter(!is.na(relsim_trin)) %>% nrow()

n_relsim_off <- d_final %>% filter(poster) %>% filter(relsim_trin<0) %>% nrow
n_relsim_sim <- d_final %>% filter(poster) %>% filter(relsim_trin==0) %>% nrow
n_relsim_on <- d_final %>% filter(poster) %>% filter(relsim_trin>0) %>% nrow

prop_relsim_off <- n_relsim_off/n_poster
prop_relsim_sim <- n_relsim_sim/n_poster
prop_relsim_on <- n_relsim_on/n_poster

prop_relsim_off+prop_relsim_sim+prop_relsim_on

prop_relsim_off %>% round(2) %>% {.*100} %>% paste0(.,"\\%") %>% writeLines(., "../results/prop_relsim_off.txt")
prop_relsim_sim %>% round(2) %>% {.*100} %>% paste0(.,"\\%") %>% writeLines(., "../results/prop_relsim_sim.txt")
prop_relsim_on %>% round(2) %>% {.*100} %>% paste0(.,"\\%") %>% writeLines(., "../results/prop_relsim_on.txt")


texreg(list("Offline > Online" = mod_h1_sub_relsim_trin_lo_adj, "Offline = Online" = mod_h1_sub_relsim_trin_0_adj, "Offline < Online" = mod_h1_sub_relsim_trin_hi_adj),
       custom.coef.names = c("Intercept", "Platform Treatment", "Age (Decades)", "5-Point Ideology", "7-Point Partisanship", "College", "POC", "Male"),
       include.ci = include.ci,
       single.row = single.row,
       float.pos = float.pos,
       tabular = tabular,
       table = table,
       file = "../results/ch3_h1_relsim_subsets.tex",
       label = "tab:ch3_h1_relsim_subsets",
       caption = "Platform Treatment Effect Heterogeneities: Outspokenness $\\times$ Relative Likemindedeness"
)

```

